### 2019-09-14 research_paper/paper1.2.tex
Add files via upload

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{amsfonts,amsmath, amssymb}
%\usepackage[spanish]{babel}
\usepackage{fancyhdr}
%\usepackage[none]{hyphenat}
\usepackage[nottoc, notlot, notlof]{tocbibind}
\usepackage{cite}
\usepackage{physics}
\usepackage{bm}
\usepackage{enumitem}
\usepackage{a4wide}
\usepackage{dsfont}
\usepackage{ amssymb }
\usepackage{cite}
\usepackage[rightcaption]{sidecap}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{ragged2e}
\usepackage{pdfpages} 
\usepackage{csquotes}
\usepackage{listings}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=blue,      
    urlcolor=blue,
    citecolor=blue,
}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Correlation between atom and cavity emissions in a driven Jaynes-Cummings system\\
%{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
%should not be used}
\thanks{corresponding author e-mail: guillermopreisser@hotmail.com}
}

\author{\IEEEauthorblockN{Guillermo Preisser and Pablo Barberis Blostein}
\IEEEauthorblockA{\textit{Instituto de Investigaciones en Matemáticas Aplicadas y en Sistemas,
} \\
\textit{Universidad Nacional Autónoma de México, Ciudad Universitaria, 04510, CDMX, México.}\\
Dated: 15 August, 2019}
}

\maketitle

\begin{abstract}
We consider a driven Jaynes-Cummings system under weak coupling, which interacts with the environment through emissions from the atom and emissions that leak through one of the lateral cavity mirrors.  We fix the parameters of the model in order to stablish a dynamic in which the number of photons in the leaky cavity remain constant and, using quantum trajectory theory, we estimate the number of spontaneous emissions in the two-level atom – which will be measured from the upper side of the cavity – by measuring emissions that leak through one of the semi-transparent cavity mirrors. Studying the system further we find that the cavity generates a correlation between the emissions from the two sources.
\end{abstract}

%the recent advances?
\section{Introduction}
Spontaneous emission is a phenomenon that has been studied formally since early XX century \cite{10.2307/94746, 1917PhyZ...18..121E}. One of the main characteristics of spontaneous emission is that, while it is known that an atom will decay exponentially, the exact time of emission, as well as the direction in  which the photon is emitted, is random, which difficults its measurement. On the other hand, photons emitted from a stimulated cavity are easy to measure, partly due the fact that we know that they leave the cavity through one of the lateral mirrors \cite{326305, doi:10.1063/1.113345}. One of the main sources for single photons are two-level atoms. However, due to the randomness of the direction in which the photons are emitted, there are difficulties in managing such sources. To sort out this difficulty one could think of a physical arrangement, in which the two-level atom is coupled to the stimulated mode of a cavity, as it is shown in Fig. \ref{asa} (b). In this physical arrangement, which is known as the driven Jaynes-Cummings model, one could try to estimate the number of spontaneous emissions of the atom, which are emitted in the upper and lower directions of the system, by measuring the photons that leak through one of the cavity mirrors, on the lateral side. In the case that a correlation exists between the two quantities, this could turn useful in the manipulation of two-level atoms as single photon sources. 
\begin{center}
\begin{figure*}\label{asa}
\begin{center}
\includegraphics[scale = 0.65]{new_image_paper.png}
%\includegraphics[scale = 0.45]{image_paper222.png}
\caption{\small{Physical arrangements of atom and atom in a cavity. In both of these arrangements we consider a source which stimulates the atom provoking it to spontaneously emit, once it decays. We consider a detector in two directions, and we keep a register of the number of photons measured in each direction. (a) In the case for the atom we don't expect a correlation between m (the number of photons measured in the upper side of the atom) and n (the number of photons measured in the right side of the atom); (b) for the atom in the cavity (a cavity with some loss rate) we study the possibility that the cavity generates a correlation between the emissions of the atom and the emissions of the cavity, which correspond to the emissions that leak through mirror 2.}} \label{probdisult}
\end{center}
\end{figure*}
\end{center}

It is easy to see why there would be no correlation between the directions of the emissions in the case for the two-level atom, without cavity. At the moment of modelling such physical system we consider a Markovian dynamic (i.e., the environment relaxes rapidly to an equilibrium state and on relevant timescales has no memory of previous interactions with the system \cite{daley2014quantum}). Given that the only way for a correlation to happen between the two emissions would be if one the emissions stay registered in the environment and, somehow, later influence the quantum system at a later time; by taking account of the Markovian dynamic we can have certainty that there is no direct correlation between the number of emissions of each source. Nevertheless, for the case of the atom coupled to a mode of a cavity, before a photon is emitted, it will most likely interact with the atom for some time. We consider the possibility that this interaction with the atom before the emission could contribute to the generation of a correlation between the emissions, which is what we study further in this paper.

In order to simulate quantum systems with dissipation and loss of coherence, like the one we deal with in this work, we use quantum trajectory theory. %Quantum trajectory was developed for various groups at the beginning of the 90's
One can define a quantum trajectory as the description of a continuously monitored quantum system conditioned on a particular past history of coherent evolution and collapse \cite{Carmichael1993Open}. These trajectories are simulated through a stochastic process, which define the times when the collapses occur.

In this work we estimate the number of spontaneous emissions by measuring stimulated emissions in an optical cavity and we calculate the existing correlation between the two emissions. This is done via quantum trajectories in which, by doing a large number of simulation and making a register of the number of spontaneous emissions and cavity emissions, we obtain probability distributions which relates these two quantities. We proceed in doing numerical calculations in order to prove that there is a correlation between two quantities, and we see how this correlation varies with respect to the cavity linewidth. \\

This article is set up as follows: A general overview of the driven Jaynes-Cummings model is presented in section two. In section three we obtain probability distributions that relate the number of spontaneous and cavity emissions. In section four we calculate the correlation between the two variables. Concluding remarks are given in section six.

%consideeron an initially ground state 0 photons

%\begin{center}
%\begin{figure}[t!]
%\begin{center}
%\includegraphics[scale = 0.45]{image_paper11.png}
%\caption{\small{Calculation of correlation using 500 time intervals, fixing $\expval{n} \approx 1$, $\gamma =$ 1.0, $g = $ 0.1, and with  $\mathcal{E} =  \kappa |\langle n \rangle|[1 + 2g^2/\gamma \kappa]$.}} \label{corrxy}
%\end{center}  
%\end{figure}
%\end{center}

%\begin{center}
%\begin{figure}[t!]
%\begin{center}
%\includegraphics[scale = 0.45]{image_paper222.png}
%\caption{\small{Calculation of correlation using 500 time intervals, fixing $\expval{n} \approx 1$, $\gamma =$ 1.0, $g = $ 0.1, and with  $\mathcal{E} =  \kappa |\langle n \rangle|[1 + 2g^2/\gamma \kappa]$.}} \label{corrxy}
%\end{center}  
%\end{figure}
%\end{center}
\section{Driven Jaynes-Cummings model}
We consider a system consisting of a two-level atom, coupled to a mode of a cavity. The mode is driven by a coherent field resonant with the atom and the mode of the cavity. In order to account for dissipation one may use a non-hermitian Hamiltonian to describe the system \cite{bla}, which will be useful at the moment of using quantum trajectory theory. Such Hamiltonian can be separated into hermitian and non-hermitian terms.
%\begin{equation}
%H = H_s - \frac{i\hbar}{2}\sum_m C^\dagger_n C_n .
%\end{equation}
The hermitian part of our Hamiltonian is given by $H_s$ which for the driven Jaynes-Cumming, under the rotating wave approximation, reads as
\begin{equation}
H_s = H_{at} + H_{cav} + H_{atcav} + H_{lascav}, \label{mainham}  
\end{equation}
where the atom and cavity terms are, respectively
\begin{subequations}
\begin{equation}
H_{at} = \tfrac{1}{2}\hbar \omega \sigma_z,    
\end{equation}
\begin{equation}
H_{cav} = \hbar \omega  a^\dagger a,  
\end{equation}
while the coupling between atom and cavity, and cavity and coherent field are
\begin{equation}
H_{atcav} = i\hbar g(a\sigma_+ - a^\dagger \sigma_-),    
\end{equation}
\begin{equation}
H_{lascav} = i\hbar \mathcal{E}(ae^{i\omega t} - a^\dagger e^{-i\omega t}),    
\end{equation}
\end{subequations}
where we introduced the coupling constant
\begin{equation}
g = \sqrt{\frac{\omega d^2}{2\hbar \epsilon_0 V_Q}},
\end{equation}
with the mode volume $V_Q$, dipolar coupling constant $d$, and $\epsilon_0$ is the permitivity of free space. $\mathcal{E}$ is a term proportional to the coherent field amplitude.
As for the non-hermitian part of our Hamiltonian, we have
\begin{equation} \label{nh}
H_{nh} = H_{dec} + H_{leak},
\end{equation}
where the terms corresponding to the spontaneous emission of the atom and the cavitty losses are
\begin{subequations}
\begin{equation}
H_{dec} = - i\hbar\frac{\gamma}{2}\sigma_+\sigma_-,
\end{equation}
\begin{equation}
H_{leak} = - i\hbar\kappa a^\dagger a.
\end{equation}
\end{subequations}
The annihilation operator $a$ of a single photon in the cavity, and the creation operator $a^\dagger$ obey $[a, a^\dagger] = 1$, while the operators $\sigma_-, \sigma_+$  account for the atomic lowering and raising operators, respectively, and the operator $\sigma_z$ accounts for the population difference between the atomic levels. These operators obey $[\sigma_+, \sigma_-] = \sigma_z, \ [\sigma_\pm, \sigma_z] = \mp 2\sigma_\pm$. $\kappa$ and $\gamma$ are the cavity loss and spontaneous decay rate.\\ %With the Hamiltonian Eq. \eqref{mainham} we can write down the master equation for the driven Jaynes-Cummings model in its Lindblad form
%\begin{equation}
%\frac{\partial \rho}{\partial t} = -\frac{i}{\hbar} [H(t), \rho]  + \mathcal{L}_\kappa \rho + \mathcal{L}_{\gamma} \rho,
%\end{equation}
%where 
%\begin{equation}
%\mathcal{L}_\kappa  \rho =  \mathcal{D}[\sqrt{2\kappa}a] \rho, 
%\end{equation}
%and
%\begin{equation}
%\mathcal{L}_\gamma \rho = \ \mathcal{D}[\sqrt{\gamma}\sigma_-] \rho,
%\end{equation}
%where $\mathcal{D}$ is a superoperator that will act on the density matrix as
%\begin{equation}
%\mathcal{D}[C] = \frac{1}{2}[2C\rho C^\dagger - C^\dagger C \rho - \rho C^\dagger   C],
%\end{equation}
%where we identify $C$ as the jump operators which will be the ones that will cause the dissipation in the system when we work using quantum trajectory theory.
%\begin{figure*}[t!]
%\includegraphics[scale = 0.8]{phases.png}
%\end{figure*}
%\begin{SCfigure*}[0.9][!h] \label{figsis}

%\includegraphics[scale = 0.8]{phases2.png}
%\caption{\small{Trayectorias cuánticas de prueba correspondientes a la ecuación maestra \eqref{masterbioptical} en el límite de acoplamiento fuerte mostrando el número promedio de fotones: $g/\kappa = 10, \gamma/2\kappa =  1$, y (a) $  \mathcal{E}/\kappa = $ 3.0; (b) $\mathcal{E}/\kappa = $ 5.0; (c) $\mathcal{E}/\kappa = $ 9.0.}}
%\label{figsis}
%\end{SCfigure*}

\section{Estimation of spontaneous emissions}
In this section we obtain estimations for the number of spontaneous emissions by measuring stimulated emission in a cavity mode in the driven Jaynes-Cummings model, using quantum trajectory theory.
\subsection{Probability distributions of emissions}
In order to get the desired estimations, first we must obtain probability distributions that relate the number of spontaneous emissions of the atom with the emissions measured from the cavity. We achieve this by making a large number of quantum  trajectories from which we keep a record of the number of spontaneous emissions and cavity losses, relating the number of spontaneous emissions for each number of cavity loss and making a probability distribution out of the emission's register of the trajectories. \\

In order to achieve this, following the procedure from quantum trajectory theory as it is explained in \cite{bla}. Starting with a state which represents a ground state of the atom with no photons in the cavity, $\ket{\phi(t = 0)} = \ket{\downarrow} \times \ket{0}$, we evolve it with the Schrödinger equation through some time $\delta t$, using a non-hermitian Hamiltonian of the form
\begin{equation}
H = H_s - \frac{i\hbar}{2}\sum_n C^\dagger_n C_n,
\end{equation}
where the operators $C_n$ are known as collapse operators.
Using a non-hermitian Hamiltonian will have as a consequence that the probability won't be conserved \cite{Sakurai:1167961}. The evolution of the state through the schrödinger equation will be interrupted by a quantum jump – an abrupt change on our state in which a photoemission has ocurred. The probability for such quantum jump to happen will be given by the collapse probability
\begin{equation} \label{probcol}
\delta p = \sum_n \delta p_n,
\end{equation}
where 
\begin{equation}
\delta p_n = \delta t \bra{\phi (t)} C^\dagger_n C_n \ket{\psi (t)}.
\end{equation}
We use these collapse probabilities to simulate the quantum trajectories, where we compare the collapse probability of eq. \eqref{probcol} with a random number $\epsilon$, uniformly distributed between zero and one. In the case the condition $\delta p > \epsilon$ is fulfilled we simulate that a quantum jump has happened, by acting with one of the collapse operators. From the non-hermitian Hamiltonian of our system \eqref{nh} we are able to identify the corresponding collapse operators which are
\begin{figure}[!t] 
\centering
\includegraphics[scale = 0.5]{distributioneng.png}
\caption{\small{Probability distribution of spontaneous emissions for different number of cavity losses in a driven Jaynes-cummings model, doing $100,000$ quantum trajectory simulations, with parameters $\mathcal{E}  = \kappa = \gamma = g = 1$.}} \label{probdiss}
\end{figure}
\begin{subequations}
\begin{equation}
C_1 = \sqrt{\gamma}\sigma_-,
\end{equation}
\begin{equation}
C_2 = \sqrt{2\kappa}a.
\end{equation}
\end{subequations}
Using equation \eqref{probcol} one can easily identify the corresponding collapse probabilities of the system. Having identified the collapse operators and the collapse probability, we simulate quantum trajectories, in which we keep count of the number of quantum jumps for each collapse operator, relating the number of quantum jumps associated to spontaneous emissions for each number of quantum jumps associated to cavity emissions until we reach a maximum number of cavity emissions, which we establish. The procedure of register of emissions is summarized in algorithm \ref{alg1}. \\

Realizing a large number of these trajectories, storing the registers in a matrix, where we keep track of the number of times that there were certain number of spontaneous emissions for each different number of cavity emission, enable us to obtain probability distributions that relate these two quantities.

In Fig.\ref{probdiss} we see the probability of obtaining different number of spontaneous emissions for different number of cavity emissions. It is clear from the plot that our probability distributions are going to be more spread out as more time (and hence more cavity emissions) pass.

\begin{algorithm}[!t]
\caption{Pseudocode for register of cavity losses and atom's spontaneous emissions}
\label{alg1}
\begin{algorithmic}
\STATE $N$: number of temporal intervals
\STATE $N_A $: number of spontaneous emissions
\STATE $N_C$: number of cavity emissions
\STATE $N_{max}$: maximum number of cavity emissions
\STATE $N_{CA}$: matrix relating the number of cavity emissions with the number of spontaneous emissions
%\STATE $K [\equiv] contador$

\STATE
\STATE Initial conditions:
\STATE $N_A = 0; N_C = 0;$
\STATE $N_{CA} = \text{zeros}(N_{max},2);  k = 0;$ 
%\STATE $\delta p > \epsilon$
%\STATE $\ket{\phi (t = 0)} = \ket{0}\otimes \ket{\downarrow}$ 
\STATE 
%\end{enumerate}
%\IF $p^T_c \geq \epsilon $
%\compute casa
%\FORALL {$i$ in $S_i$}
%\IF
%\IF {$\delta p > \epsilon$}

%\FOR{$i = 1$ to N} 
%\STATE $\ket{ \phi^1(t + \delta t)} = e^{-iH\delta t/\hbar}\ket{\phi (t)}$
%\STATE$ \delta p_1 = \delta t\bra{\phi(t)}C^\dagger_1 C_1\ket{\phi(t)}$
%\STATE $ \delta p_2 =  \delta t\bra{\phi(t)}C^\dagger_2 C_2\ket{\phi(t)}$
%\STATE $\delta p = \delta p_1 + \delta p_2$
\FOR{$i = 1$ to N} 
\STATE $\ket{ \phi^1(t + \delta t)} = e^{-iH\delta t/\hbar}\ket{\phi (t)}$
\STATE$ \delta p_1 = \delta t\bra{\phi(t)}C^\dagger_1 C_1\ket{\phi(t)}$
\STATE $ \delta p_2 =  \delta t\bra{\phi(t)}C^\dagger_2 C_2\ket{\phi(t)}$
\STATE $\delta p = \delta p_1 + \delta p_2$
\IF {$\delta p > \epsilon$}
\IF{$ \tfrac{\delta p_1}{\delta p} > \epsilon$}
\STATE $\ket{\phi (t + \delta t)} = \frac{C_1 \ket{ \ \phi(t)}}{\sqrt \frac{\delta p_1}{\delta t}}$
\STATE $N_A = N_A + 1$
\ELSE
\STATE $\ket{\phi (t + \delta t)} = \frac{C_2 \ket{ \ \phi(t)}}{\sqrt \frac{\delta p_2}{\delta t}}$
\STATE $N_C = N_C + 1$
\STATE $N_{CA}[k+1,1] = N_C$
\STATE  $N_{CA}[k+1,2] = N_A$
\STATE $k = k+1$
\IF{$N_C == N_{max}$}
\STATE \textbf{\textit{break}}
\ENDIF
%\STATE $x$ was less than the minimum threshold
\ENDIF
\ELSE
\STATE $\ket{ \phi(t + \delta t)} = \frac{\ket{\phi^1 (t+ \delta t)}}{\sqrt{1-\delta p}}$
\STATE $t \ += \delta t$
\ENDIF
\ENDFOR
\RETURN  $N_{CA}$
%\STATE $t \ += \delta t$
%\ENDFOR
%\ENDIF
%\ENDIF
%\ENDFOR
%\end{enumerate}
\end{algorithmic}
%\caption{Algoritmo para obtener distribución de probabilidad de número de emisiones espontáneas}
\end{algorithm}

\begin{center}
\begin{figure*}[!t]\label{error2}
\begin{center}
\includegraphics[scale = 0.55]{newerrorppp.png}
\caption{\small{(a) Probability distributions for different mean number of spontaneous emissions $\mu$; (b) Calculation of variance with respect to the mean number of sponatenous emissions $\mu$. In both cases we consider $\expval{n} \approx 1$, $\gamma = 1.0$ , $\kappa = g = 0.1$ and $\mathcal{E} =  \kappa |\langle n \rangle|[1 + 2g^2/\gamma \kappa]$.}} \label{probdisult}
\end{center}
\end{figure*}
\end{center}
\subsection{Extracting data from the probability distributions}
Due to the complex dynamic of the driven Jaynes-Cummings system \cite{Carmichael1993Open}, it is important to know the dynamic that the system undergoes at the moment of obtaining the probability distributions, in order to have a better physical understanding of our results. In this case we opt for fixing the number of photons in the cavity.

We do this by solving what is known as the Maxwell-Bloch equations, which give the dynamic of our system for the variables  $\expval{a}, \expval{\sigma_-}$ and $\expval{\sigma_z}$ that correspond to the cavity field, atomic coherence, and atomic inversion respectively \cite{Alsing_1991}. For the case of the driven Jaynes-Cummings system, these equations are given by
\begin{subequations} \label{maxbloch}
\begin{equation} \label{bloch1}
\dot{z} = (g/2)v + \mathcal{E} - \kappa z,
\end{equation}
\begin{equation} \label{bloch2}
\dot{v} = gmz - (\gamma/2)v,
\end{equation}
\begin{equation} \label{bloch3}
\dot{m} = -2g(z^*v + v^*z) - \gamma(m + 2),
\end{equation}
\end{subequations} 
where we defined  $z = e^{i\omega t}\expval{a}$, $v = 2e^{i\omega t}\expval{\sigma_-}$ and $m = 2\expval{\sigma_z}$. Solving for the case in which our variables are constant we can obtain steady state solutions \cite{gagniuc2017markov}.  From \eqref{bloch1} one can obtain the equation
\begin{equation} \label{chaf1}
\expval{a}_{ss} = \frac{\mathcal{E}e^{-i\omega t} + g\expval{\sigma_-}_{ss}}{\kappa}.
\end{equation}
While from \eqref{bloch2} and \eqref{bloch3} one obtains
\begin{equation} \label{chaf2}
\expval{\sigma_-}_{ss} = -\frac{2g}{\gamma}\frac{\expval{a}_{ss}}{1 + \frac{8g^2}{\gamma^2}|\expval{a}_{ss}|^2}.
\end{equation}
The requirement that both \eqref{chaf1} and \eqref{chaf2} are valid gives as result
\begin{equation}
\bigg(\frac{\mathcal{E}}{\kappa}\bigg)^2 = |\expval{a}_{ss}|^2 \bigg(1 + \frac{2g^2}{\gamma \kappa}\frac{1}{1 + \frac{8g^2}{\gamma^2}|\expval{a}_{ss}|^2}\bigg)^2.
\end{equation}
Considering $\gamma \gg g$, it is possible to clear $|\expval{a}|^2$, which allow us to obtain an expression for the expected value of the number of photons in the cavity
\begin{equation} \label{numfo}
|\expval{a}_{ss}|^2 = \bigg(\frac{\mathcal{E}/\kappa}{1 + 2g^2/\gamma \kappa}\bigg)^2.
\end{equation}
\begin{figure}[!t]  
\centering
\includegraphics[scale = 0.45]{newsigmaeng.png}
\caption{\small{Average number of spontaneous emissions $\pm \sigma$ with respect to cavity emissions, under parameters $\expval{n} \approx 1$, $\gamma = 1$ , $\kappa = g = 0.1$ and $\mathcal{E} =  \kappa |\langle n \rangle|[1 + 2g^2/\gamma \kappa]$.}}
\label{graph}
\end{figure} 
Having Eq. \eqref{numfo} we are able to stablish a dynamic in the system in which we fix the number of photons. Fixing the photon number to one and leaving $\mathcal{E}$ as a free parameter, we obtain probability distributions of the number of spontaneous emissions $E_i$ for different mean number of spontaneous emissions just as we see in Fig. \ref{probdisult} (a). From these probability distributions we can calculate the variance and graph it against the mean value as we see in Fig. \ref{probdisult} (b), where we obtain a variance almost equal to the mean value, something which is characteristic of Poisson distributions. 
Finally we can graph the mean value of spontaneous emissions against the number of cavity emissions considering standard deviation in order to have a better grasp of the certainty in the estimations, something that is shown in Fig. \ref{graph}.

\section{Correlation between atom and cavity emissions}
So far we have obtained estimations for the number of spontaneous emission for each measured number of cavity emissions. From our results it is obvious how the number of spontaneous emissions will increase with respect to the number of cavity emissions, given that more time will pass and more emissions will occur. One can also see how increasing the cavity linewidth $\kappa$ and keeping the other parameters constant will translate into a decrease of spontaneous emissions with respect to the number of cavity emissions. However, one question remains: is there a direct correlation between these two quantities? If yes, how this varies with respect to the cavity linewidth. From the beginning one could expect that in the case for a big $\kappa$ there would be no correlation at all, since this situation will be equivalent to the situation where there is no cavity.

In order to have a measure of the correlation of the emissions we introduce the Pearson Correlation Coefficient \cite{benesty2009pearson}
\begin{equation} 
r_{xy} = \frac{\sum\limits_{i=1}^n(x_i - \bar{x})(y_i - \bar{y})}{\sqrt{\sum\limits_{i=1}^n(x_i - \bar{x})^2\sum\limits_{i=1}^n(y_i - \bar{y})^2}}.  \label{correlationc}
\end{equation}
Having an equation that gives us a measure of the correlation, now we want the necessary data in order to obtain information about the correlation between the two types of emissions that we deal with. We can obtain this data by defining a temporal interval from which we make a register of the final number of spontaneous and cavity emissions. Given that what we are doing are essentially stochastic calculations, there will be variations in the final number of emissions for each trajectory. Making a large number of trajectories keeping track of the final number of emissions and pluggin the data in \eqref{correlationc} we are able to calculate the correlation.

\begin{center}
\begin{figure}[t!]
\begin{center}
\includegraphics[scale = 0.45]{cor_2.png}
\caption{\small{Calculation of correlation using 500 time intervals, fixing $\expval{n} \approx 1$, $\gamma =$ 1.0, $g = $ 0.1, and with  $\mathcal{E} =  \kappa |\langle n \rangle|[1 + 2g^2/\gamma \kappa]$.}} \label{corrxy}
\end{center}  
\end{figure}
\end{center}

\begin{center}
\begin{figure}[h!]
\begin{center}
\includegraphics[scale = 0.45]{difftimes12.png}
\caption{\small{Correlation using different temporal intervals, fixing $\expval{n} \approx 1$, $\gamma =$ 1.0, $g =$ 0.1, and with  $\mathcal{E} =  \kappa |\langle n \rangle|[1 + 2g^2/\gamma \kappa]$.}}  \label{errorzz}
\end{center}
\end{figure}
\end{center}
%kncrease or increases
From Fig. \ref{corrxy} we see that, as we expected, the correlation goes to zero as we increase the cavity linewidth. Nonetheless, perhaps a more interesting question is: how high can this correlation be? Trying with values for $\kappa/\gamma$ lower than $0.1$, we notice that the correlation's increase stops and a decrease begins. It is possible that this stop in the increase of the correlation is due to the fact that if we keep decreasing the cavity linewidth it will come a point where the number of emissions will decrease considerably, diminishing the correlation. If this is the case we should expect that as we increase the temporal intervals, %the cavity linewidth at which the correlation starts decreasing should be smaller.
we also see an increment of the correlation.

%In Fig. \ref{errorzz} we can appreciate that, as we increase the total temporal interval, the cavity linewidth at which the correlation starts decreasing is smaller. This supports the idea that the time that takes for the system in stablishing the number photons will affect the minimum value of cavity linewidth at which the correlation starts decreasing.

In Fig. \ref{errorzz} we can appreciate that, as we increase the total temporal interval, there is also a slight increase in the correlation. This supports the idea that the time that takes for the system in stablishing the number photons will affect the value for the correlation, for values of $\kappa/\gamma$ lower than $0.1$.

\section{Conclusions}
In this work we considered a driven Jaynes-Cummings system. We made a program in which, through the use of quantum trajectory theory, we were able to obtain probability distributions that relate the number of spontaneous emissions given certain number of cavity emissions. Through the probability distributions we obtained estimations for the number of spontaneous emissions by measuring cavity emissions, considering the correspondent error. Finally we study the existing correlation where we saw how this correlation decreases as we increase the cavity linewidth. However, if we try with values for  $\kappa/\gamma < 0.1$, there comes a point where the increase stops and we see a decrease. We believe this is related to the fact that if we use enough small values of $\kappa$ there will come a point where the emission of photons will be too low and this will imply a decrease in the correlation. The results in this work provide a tool that could be useful in the manipulation of single photons product of spontaneous emission, and provide insight into the physical behavior of the driven Jaynes-Cummings model.

\section*{Acknowledgment}

Support by UNAM, projects CONACyT and UNAMPAPIIT IG100518.

\bibliographystyle{IEEEtran}
\bibliography{reftesis}
\end{document}

### 2019-09-17 research_paper/paper1.2.tex
Update paper1.2.tex
Add files via upload

@@
 The mode is driven by a coherent field resonant with the atom and the mode of the cavity.
-In order to account for dissipation one may use a non-hermitian Hamiltonian to describe the system \cite{bla}, which will be useful at the moment of using quantum trajectory theory.
+In order to account for dissipation one may use a non-hermitian Hamiltonian to describe the system \cite{bla}.
+Using this description for the system will turn useful at the moment of using quantum trajectory theory.
 Such Hamiltonian can be separated into hermitian and non-hermitian terms.
@@
 \end{subequations}
-The annihilation operator $a$ of a single photon in the cavity, and the creation operator $a^\dagger$ obey $[a, a^\dagger] = 1$, while the operators $\sigma_-, \sigma_+$  account for the atomic lowering and raising operators, respectively, and the operator $\sigma_z$ accounts for the population difference between the atomic levels.
+The annihilation operator $a$ of a single photon in the cavity, and the creation operator $a^\dagger$ obey $[a, a^\dagger] = 1$.
+The operators $\sigma_-, \sigma_+$  account for the atomic lowering and raising operators, respectively, and the operator $\sigma_z$ accounts for the population difference between the atomic levels.
 These operators obey $[\sigma_+, \sigma_-] = \sigma_z, \ [\sigma_\pm, \sigma_z] = \mp 2\sigma_\pm$.
@@
 We achieve this by making a large number of quantum  trajectories from which we keep a record of the number of spontaneous emissions and cavity losses, relating the number of spontaneous emissions for each number of cavity loss and making a probability distribution out of the emission's register of the trajectories.
-\\
 
@@
 where 
-\begin{equation}
+\begin{equation} \label{relprob}
 \delta p_n = \delta t \bra{\phi (t)} C^\dagger_n C_n \ket{\psi (t)}.
@@
 In the case the condition $\delta p > \epsilon$ is fulfilled we simulate that a quantum jump has happened, by acting with one of the collapse operators.
+The operator with which we'll act on the state will be given according to the relative probabilities of eq.
+\eqref{relprob}.
 From the non-hermitian Hamiltonian of our system \eqref{nh} we are able to identify the corresponding collapse operators which are
@@
 The procedure of register of emissions is summarized in algorithm \ref{alg1}.
-\\
 

### 2019-11-09 paper1.2.1.tex
Add files via upload
Commit intermedio, muchos cambios hechos por pablo

--- 2019-09-17 research_paper/paper1.2.tex
@@
 \usepackage{bm}
+\usepackage[draft,inline,nomargin]{fixme} \fxsetup{theme=color}
 \usepackage{enumitem}
@@
 
-\title{Correlation between atom and cavity emissions in a driven Jaynes-Cummings system\\
+\title{Correlation between different emission channels from an atom inside a leaky driven cavity\\
 %{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
@@
 \begin{abstract}
-We consider a driven Jaynes-Cummings system under weak coupling, which interacts with the environment through emissions from the atom and emissions that leak through one of the lateral cavity mirrors.
-We fix the parameters of the model in order to stablish a dynamic in which the number of photons in the leaky cavity remain constant and, using quantum trajectory theory, we estimate the number of spontaneous emissions in the two-level atom – which will be measured from the upper side of the cavity – by measuring emissions that leak through one of the semi-transparent cavity mirrors.
-Studying the system further we find that the cavity generates a correlation between the emissions from the two sources.
+  A two level atom in free space does not show any correlation between
+  photons emitted in different directions. We consider a two level
+  atom inside a driven leaky cavity. We consider two atomic emission
+  channels: emission to cavity modes and emission to no-cavity modes.
+  Using the quantum trajectory formalism we study the correlation
+  between photons emitted into cavity modes and that leak the cavity
+  through its mirror, with photons that are emitted into the rest of
+  the modes. We find that the cavity generates a correlation between
+  the two emission channels.
 \end{abstract}
@@
 \section{Introduction}
-Spontaneous emission is a phenomenon that has been studied formally since early XX century \cite{10.2307/94746, 1917PhyZ...18..121E}.
-One of the main characteristics of spontaneous emission is that, while it is known that an atom will decay exponentially, the exact time of emission, as well as the direction in  which the photon is emitted, is random, which difficults its measurement.
-On the other hand, photons emitted from a stimulated cavity are easy to measure, partly due the fact that we know that they leave the cavity through one of the lateral mirrors \cite{326305, doi:10.1063/1.113345}.
-One of the main sources for single photons are two-level atoms.
-However, due to the randomness of the direction in which the photons are emitted, there are difficulties in managing such sources.
-To sort out this difficulty one could think of a physical arrangement, in which the two-level atom is coupled to the stimulated mode of a cavity, as it is shown in Fig.
-\ref{asa} (b).
-In this physical arrangement, which is known as the driven Jaynes-Cummings model, one could try to estimate the number of spontaneous emissions of the atom, which are emitted in the upper and lower directions of the system, by measuring the photons that leak through one of the cavity mirrors, on the lateral side.
-In the case that a correlation exists between the two quantities, this could turn useful in the manipulation of two-level atoms as single photon sources.
+Spontaneous emission is a phenomenon that has been studied since the
+early XX century \cite{10.2307/94746, 1917PhyZ...18..121E}. One of the
+main characteristics of spontaneous emission is that
+\fxnote{spontaneus emission no es exponencial, es aproximadamente
+  exponencial, si quitas la aproximacion markoviana te queda una cola
+  polinomial, quite la oracion} the exact time of emission, as well as
+the direction in which the photon is emitted, is random, which
+difficults its measurement. On the other hand, photons emitted from a
+cavity are easy to measure, partly due the fact that we know that they
+leave the cavity through one of the lateral mirrors \cite{326305,
+  doi:10.1063/1.113345}. The randomness of the direction in which the
+photons are emitted by atoms in free space difficults photon counting
+experiments. To sort out this difficulty one could think of a physical
+arrangement, in which the two-level atom is coupled to the stimulated
+mode of a cavity, as it is shown in Fig. \ref{asa} (b). In this
+physical arrangement, \fxnote*{tienes una cita donde lo nombren
+  asi?}{which is known as the driven Jaynes-Cummings model}, one could
+try to estimate the number of spontaneous emissions of the atom
+--which are emitted in modes that are not cavity modes and therefore
+escape the cavity-- by measuring the photons that leak through one of
+the cavity mirrors. In the case that a
+correlation exists between the two quantities, we can count the number
+of photons that leak the cavity through its mirror, which is easy to
+measure, to find information about the number of photons emitted into
+the other modes (spontaneus emission), which are difficult to measure.
 \begin{center}
@@
 \begin{center}
-\includegraphics[scale = 0.65]{new_image_paper.png}
+\includegraphics[scale = 0.65]{newimagepaper.pdf}
 %\includegraphics[scale = 0.45]{image_paper222.png}
-\caption{\small{Physical arrangements of atom and atom in a cavity.
-In both of these arrangements we consider a source which stimulates the atom provoking it to spontaneously emit, once it decays.
-We consider a detector in two directions, and we keep a register of the number of photons measured in each direction.
-(a) In the case for the atom we don't expect a correlation between m (the number of photons measured in the upper side of the atom) and n (the number of photons measured in the right side of the atom); (b) for the atom in the cavity (a cavity with some loss rate) we study the possibility that the cavity generates a correlation between the emissions of the atom and the emissions of the cavity, which correspond to the emissions that leak through mirror 2.}} \label{probdisult}
+\caption{\small{Physical arrangements of atom and atom in a cavity. In
+    both of these arrangements we consider a source which stimulates
+    the atom provoking it to spontaneously emit, once it decays. We
+    consider a detector in two directions, and we keep a register of
+    the number of photons measured in each direction. (a) In the case
+    for the atom we don't expect a correlation between m (the number
+    of photons measured in the upper side of the atom) and n (the
+    number of photons measured in the right side of the atom); (b) for
+    the atom in the cavity (a cavity with some loss rate) we study the
+    possibility that the cavity generates a correlation between the
+    emissions of the atom and the emissions of the cavity, which
+    correspond to the emissions that leak through mirror
+    2.}} \label{probdisult}
 \end{center}
@@
 
-It is easy to see why there would be no correlation between the directions of the emissions in the case for the two-level atom, without cavity.
-At the moment of modelling such physical system we consider a Markovian dynamic (i.e., the environment relaxes rapidly to an equilibrium state and on relevant timescales has no memory of previous interactions with the system \cite{daley2014quantum}).
-Given that the only way for a correlation to happen between the two emissions would be if one the emissions stay registered in the environment and, somehow, later influence the quantum system at a later time; by taking account of the Markovian dynamic we can have certainty that there is no direct correlation between the number of emissions of each source.
-Nevertheless, for the case of the atom coupled to a mode of a cavity, before a photon is emitted, it will most likely interact with the atom for some time.
-We consider the possibility that this interaction with the atom before the emission could contribute to the generation of a correlation between the emissions, which is what we study further in this paper.
+In the case of a two-level atom in free space, the absence of
+correlation between different channels is the result of the markovian
+approximation, which assumes that the environment has no memory of
+previous interactions with the system \cite{daley2014quantum}. Two
+atomic emissions would be correlated if one of the emissions stay
+registered in the environment and, somehow, influence the second
+emission of a two-level atom at a later time; the Markovian
+approximation does not allow memory effects and there is no
+correlation between the number of emissions of each source: knowing
+the number of photons emitted in some region of the space during some
+time does not give me any information on the number of photons emitted
+in other region of the space. Nevertheless, for the case of an atom
+inside a cavity, before a photon leaks the cavity, it will interact
+with the atom for some time. This interaction with the atom before the
+emission generates a correlation between photons that leak the cavity
+through its mirror and photons that leak the cavity through its side.
 
-In order to simulate quantum systems with dissipation and loss of coherence, like the one we deal with in this work, we use quantum trajectory theory.
-%Quantum trajectory was developed for various groups at the beginning of the 90's
-One can define a quantum trajectory as the description of a continuously monitored quantum system conditioned on a particular past history of coherent evolution and collapse \cite{Carmichael1993Open}.
-These trajectories are simulated through a stochastic process, which define the times when the collapses occur.
+We use quantum trajectory theory to theoretically calculate the
+correlation between different emission channels. A quantum trajectory
+is the description of a continuously monitored quantum system
+conditioned on a particular past history of coherent evolution and
+collapse \cite{Carmichael1993Open}. These trajectories are simulated
+through a stochastic process, which define the times when the
+collapses occur. Each trajectory gives us the number of photon emitted
+in each channel. Simulating a large number of trajectories and
+registering the number of photon emissions into the two channels, we
+obtain its correlation. The correlation varies with the cavity
+linewidth and the atom-cavity coupling. For a very bad cavity we
+recover the free space result: there is no correlation between the two
+channels.
 
-In this work we estimate the number of spontaneous emissions by measuring stimulated emissions in an optical cavity and we calculate the existing correlation between the two emissions.
-This is done via quantum trajectories in which, by doing a large number of simulation and making a register of the number of spontaneous emissions and cavity emissions, we obtain probability distributions which relates these two quantities.
-We proceed in doing numerical calculations in order to prove that there is a correlation between two quantities, and we see how this correlation varies with respect to the cavity linewidth.
-\\
+This article is organized as follows: A general overview of the driven
+Jaynes-Cummings model is presented in section \ref{sc:drivenjc}. In
+section \ref{sc:distributions} we obtain probability distributions
+that relate the number of spontaneous and cavity emissions. In section
+\ref{sc:correlation} we calculate the correlation between the two variables.
+Concluding remarks are given in section \ref{sc:conclusions}
 
-This article is set up as follows: A general overview of the driven Jaynes-Cummings model is presented in section two.
-In section three we obtain probability distributions that relate the number of spontaneous and cavity emissions.
-In section four we calculate the correlation between the two variables.
-Concluding remarks are given in section six.
-
-%consideeron an initially ground state 0 photons
-
-%\begin{center}
-%\begin{figure}[t!]
-%\begin{center}
-%\includegraphics[scale = 0.45]{image_paper11.png}
-%\caption{\small{Calculation of correlation using 500 time intervals, fixing $\expval{n} \approx 1$, $\gamma =$ 1.0, $g = $ 0.1, and with  $\mathcal{E} =  \kappa |\langle n \rangle|[1 + 2g^2/\gamma \kappa]$.}} \label{corrxy}
-%\end{center}  
-%\end{figure}
-%\end{center}
-
-%\begin{center}
-%\begin{figure}[t!]
-%\begin{center}
-%\includegraphics[scale = 0.45]{image_paper222.png}
-%\caption{\small{Calculation of correlation using 500 time intervals, fixing $\expval{n} \approx 1$, $\gamma =$ 1.0, $g = $ 0.1, and with  $\mathcal{E} =  \kappa |\langle n \rangle|[1 + 2g^2/\gamma \kappa]$.}} \label{corrxy}
-%\end{center}  
-%\end{figure}
-%\end{center}
-\section{Driven Jaynes-Cummings model}
-We consider a system consisting of a two-level atom, coupled to a mode of a cavity.
-The mode is driven by a coherent field resonant with the atom and the mode of the cavity.
-In order to account for dissipation one may use a non-hermitian Hamiltonian to describe the system \cite{bla}.
-Using this description for the system will turn useful at the moment of using quantum trajectory theory.
-Such Hamiltonian can be separated into hermitian and non-hermitian terms.
+\section{Driven Jaynes-Cummings model}\label{sc:drivenjc}
+We consider a system consisting of a two-level atom, coupled to a mode
+of a leaky cavity. The mode is driven by a coherent field resonant
+with the atomic transition and the cavity mode.
+% In order to account for
+% dissipation one may use a non-hermitian Hamiltonian to describe the
+% system \cite{bla}. Using this description for the system will turn
+% useful at the moment of using quantum trajectory theory. Such
+% Hamiltonian can be separated into hermitian and non-hermitian terms.
 %\begin{equation}
@@
 %\end{equation}
-The hermitian part of our Hamiltonian is given by $H_s$ which for the driven Jaynes-Cumming, under the rotating wave approximation, reads as
+The Hamiltonian of this system, in the rotating wave approximation is
+given by
 \begin{equation}
@@
 \end{equation}
-while the coupling between atom and cavity, and cavity and coherent field are
+while the coupling between atom and cavity, and cavity and coherent
+field are
 \begin{equation}
@@
 \end{subequations}
-where we introduced the coupling constant
+where the annihilation operator $a$ of a single photon in the cavity,
+and the creation operator $a^\dagger$ obey $[a, a^\dagger] = 1$. The
+operators $\sigma_-, \sigma_+$ account for the atomic lowering and
+raising operators, respectively, and the operator $\sigma_z$ accounts
+for the population difference between the atomic levels. These
+operators obey
+$[\sigma_+, \sigma_-] = \sigma_z, \ [\sigma_\pm, \sigma_z] = \mp
+2\sigma_\pm$. The strength of the coupling between atom and cacity
+field is given by the constant
 \begin{equation}
@@
 \end{equation}
-with the mode volume $V_Q$, dipolar coupling constant $d$, and $\epsilon_0$ is the permitivity of free space. $\mathcal{E}$ is a term proportional to the coherent field amplitude.
-As for the non-hermitian part of our Hamiltonian, we have
+where $V_Q$ is the mode volume , $d$ is the atomic dipole , and
+$\epsilon_0$ is the permitivity of free space. $\mathcal{E}$ is a term
+proportional to the coherent field amplitude. Dissipation is
+introduced by the following non-hermitian Hamiltonian
 \begin{equation} \label{nh}
@@
 \end{equation}
-where the terms corresponding to the spontaneous emission of the atom and the cavitty losses are
+where the terms corresponding to spontaneous emission of the atom and cavity losses are
 \begin{subequations}
@@
 \begin{equation}
-H_{leak} = - i\hbar\kappa a^\dagger a.
+H_{leak} = - i\hbar\kappa a^\dagger a\, .
 \end{equation}
 \end{subequations}
-The annihilation operator $a$ of a single photon in the cavity, and the creation operator $a^\dagger$ obey $[a, a^\dagger] = 1$.
-The operators $\sigma_-, \sigma_+$  account for the atomic lowering and raising operators, respectively, and the operator $\sigma_z$ accounts for the population difference between the atomic levels.
-These operators obey $[\sigma_+, \sigma_-] = \sigma_z, \ [\sigma_\pm, \sigma_z] = \mp 2\sigma_\pm$.
-$\kappa$ and $\gamma$ are the cavity loss and spontaneous decay rate.\\ %With the Hamiltonian Eq.
-\eqref{mainham} we can write down the master equation for the driven Jaynes-Cummings model in its Lindblad form
-%\begin{equation}
-%\frac{\partial \rho}{\partial t} = -\frac{i}{\hbar} [H(t), \rho]  + \mathcal{L}_\kappa \rho + \mathcal{L}_{\gamma} \rho,
-%\end{equation}
-%where 
-%\begin{equation}
-%\mathcal{L}_\kappa  \rho =  \mathcal{D}[\sqrt{2\kappa}a] \rho, 
-%\end{equation}
-%and
-%\begin{equation}
-%\mathcal{L}_\gamma \rho = \ \mathcal{D}[\sqrt{\gamma}\sigma_-] \rho,
-%\end{equation}
-%where $\mathcal{D}$ is a superoperator that will act on the density matrix as
-%\begin{equation}
-%\mathcal{D}[C] = \frac{1}{2}[2C\rho C^\dagger - C^\dagger C \rho - \rho C^\dagger   C],
-%\end{equation}
-%where we identify $C$ as the jump operators which will be the ones that will cause the dissipation in the system when we work using quantum trajectory theory.
-%\begin{figure*}[t!]
-%\includegraphics[scale = 0.8]{phases.png}
-%\end{figure*}
-%\begin{SCfigure*}[0.9][!h] \label{figsis}
+where $\kappa$ and $\gamma$ are the cavity loss and spontaneous decay
+rate. The evolution between jumps is given by $H=H_s+H_{nh}$. This
+evolution is interrumped by spontaneus emission by the atom or when a
+photon leaks the cavity.
 
-%\includegraphics[scale = 0.8]{phases2.png}
-%\caption{\small{Trayectorias cuánticas de prueba correspondientes a la ecuación maestra \eqref{masterbioptical} en el límite de acoplamiento fuerte mostrando el número promedio de fotones: $g/\kappa = 10, \gamma/2\kappa =  1$, y (a) $  \mathcal{E}/\kappa = $ 3.0; (b) $\mathcal{E}/\kappa = $ 5.0; (c) $\mathcal{E}/\kappa = $ 9.0.}}
-%\label{figsis}
-%\end{SCfigure*}
-
-\section{Estimation of spontaneous emissions}
-In this section we obtain estimations for the number of spontaneous emissions by measuring stimulated emission in a cavity mode in the driven Jaynes-Cummings model, using quantum trajectory theory.
-\subsection{Probability distributions of emissions}
-In order to get the desired estimations, first we must obtain probability distributions that relate the number of spontaneous emissions of the atom with the emissions measured from the cavity.
-We achieve this by making a large number of quantum  trajectories from which we keep a record of the number of spontaneous emissions and cavity losses, relating the number of spontaneous emissions for each number of cavity loss and making a probability distribution out of the emission's register of the trajectories.
-
-In order to achieve this, following the procedure from quantum trajectory theory as it is explained in \cite{bla}.
-Starting with a state which represents a ground state of the atom with no photons in the cavity, $\ket{\phi(t = 0)} = \ket{\downarrow} \times \ket{0}$, we evolve it with the Schrödinger equation through some time $\delta t$, using a non-hermitian Hamiltonian of the form
+We now summarize te quantum trajectory formalism \cite{bla} that we
+use to solve the system. We start with a state which represents a
+ground state of the atom with no photons in the cavity,
+$\ket{\phi(t = 0)} = \ket{\downarrow} \times \ket{0}$, we evolve it
+with the Schrödinger equation through some time $\delta t$, using the
+non-hermitian Hamiltonian
 \begin{equation}
-H = H_s - \frac{i\hbar}{2}\sum_n C^\dagger_n C_n,
+H = H_s +H_{nh}\, .
 \end{equation}
-where the operators $C_n$ are known as collapse operators.
-Using a non-hermitian Hamiltonian will have as a consequence that the probability won't be conserved \cite{Sakurai:1167961}.
-The evolution of the state through the schrödinger equation will be interrupted by a quantum jump – an abrupt change on our state in which a photoemission has ocurred.
-The probability for such quantum jump to happen will be given by the collapse probability
+Using a non-hermitian Hamiltonian will have as a consequence that the
+probability won't be conserved \cite{Sakurai:1167961}. The evolution
+of the state through the schrödinger equation will be interrupted by a
+quantum jump – an abrupt change on our state in which a photoemission
+has ocurred. The probability for such quantum jump to happen will be
+given by the collapse probability
 \begin{equation} \label{probcol}
@@
 where 
-\begin{equation} \label{relprob}
-\delta p_n = \delta t \bra{\phi (t)} C^\dagger_n C_n \ket{\psi (t)}.
-\end{equation}
-We use these collapse probabilities to simulate the quantum trajectories, where we compare the collapse probability of eq.
-\eqref{probcol} with a random number $\epsilon$, uniformly distributed between zero and one.
-In the case the condition $\delta p > \epsilon$ is fulfilled we simulate that a quantum jump has happened, by acting with one of the collapse operators.
-The operator with which we'll act on the state will be given according to the relative probabilities of eq.
-\eqref{relprob}.
-From the non-hermitian Hamiltonian of our system \eqref{nh} we are able to identify the corresponding collapse operators which are
+\begin{eqnarray} \label{relprob}
+\delta p_1 &=& \gamma \bra{\phi (t)} \sigma_+
+               \sigma_-\ket{\psi (t)}\delta t \\
+  \delta p_2 &=& 2\kappa \bra{\phi (t)} a^\dagger a\ket{\psi (t)}\delta t 
+\end{eqnarray}
+We use these collapse probabilities to simulate the quantum
+trajectories, where we compare the collapse probability of eq.
+\eqref{probcol} with a random number $\epsilon$, uniformly distributed
+between zero and one. In the case the condition $\delta p > \epsilon$
+is fulfilled we simulate that a quantum jump has happened, by acting
+with one of the collapse operators. The operator with which we'll act
+on the state will be given according to the relative probabilities of
+eq. \eqref{relprob}.
 \begin{figure}[!t] 
 \centering
-\includegraphics[scale = 0.5]{distributioneng.png}
+\includegraphics[scale = 0.5]{distributioneng.pdf}
 \caption{\small{Probability distribution of spontaneous emissions for different number of cavity losses in a driven Jaynes-cummings model, doing $100,000$ quantum trajectory simulations, with parameters $\mathcal{E}  = \kappa = \gamma = g = 1$.}} \label{probdiss}
 \end{figure}
-\begin{subequations}
-\begin{equation}
-C_1 = \sqrt{\gamma}\sigma_-,
-\end{equation}
-\begin{equation}
-C_2 = \sqrt{2\kappa}a.
-\end{equation}
-\end{subequations}
-Using equation \eqref{probcol} one can easily identify the corresponding collapse probabilities of the system.
-Having identified the collapse operators and the collapse probability, we simulate quantum trajectories, in which we keep count of the number of quantum jumps for each collapse operator, relating the number of quantum jumps associated to spontaneous emissions for each number of quantum jumps associated to cavity emissions until we reach a maximum number of cavity emissions, which we establish.
-The procedure of register of emissions is summarized in algorithm \ref{alg1}.
+Using equation \eqref{probcol} one can easily identify the
+corresponding collapse probabilities of the system. Having identified
+the collapse operators and the collapse probability, we simulate
+quantum trajectories, in which we keep count of the number of quantum
+jumps for each collapse operator, relating the number of quantum jumps
+associated to spontaneous emissions for each number of quantum jumps
+associated to cavity emissions until we reach a maximum number of
+cavity emissions, which we establish. The procedure of register of
+emissions is summarized in algorithm \ref{alg1}.
 
-Realizing a large number of these trajectories, storing the registers in a matrix, where we keep track of the number of times that there were certain number of spontaneous emissions for each different number of cavity emission, enable us to obtain probability distributions that relate these two quantities.
+Realizing a large number of these trajectories, storing the registers
+in a matrix, where we keep track of the number of times that there
+were certain number of spontaneous emissions for each different number
+of cavity emission, enable us to obtain probability distributions that
+relate these two quantities.
+
+\section{Counting photons emitted in different channels}\label{sc:distributions}
+In this section we use the quantum trajectory formalism to calculate
+the distribution probability of the number of spontaneous emissions by
+the atom conditioned to the number of photons that leaked the cavity
+from its mirror .
+\subsection{Probability distributions of emissions}
 
@@
 \STATE $N_{CA} = \text{zeros}(N_{max},2);  k = 0;$
-%\STATE $\delta p > \epsilon$
-%\STATE $\ket{\phi (t = 0)} = \ket{0}\otimes \ket{\downarrow}$ 
+
 \STATE
-%\end{enumerate}
-%\IF $p^T_c \geq \epsilon $
-%\compute casa
-%\FORALL {$i$ in $S_i$}
-%\IF
-%\IF {$\delta p > \epsilon$}
 
-%\FOR{$i = 1$ to N} 
-%\STATE $\ket{ \phi^1(t + \delta t)} = e^{-iH\delta t/\hbar}\ket{\phi (t)}$
-%\STATE$ \delta p_1 = \delta t\bra{\phi(t)}C^\dagger_1 C_1\ket{\phi(t)}$
-%\STATE $ \delta p_2 =  \delta t\bra{\phi(t)}C^\dagger_2 C_2\ket{\phi(t)}$
-%\STATE $\delta p = \delta p_1 + \delta p_2$
 \FOR{$i = 1$ to N} 
@@
 \ENDIF
-%\STATE $x$ was less than the minimum threshold
+
 \ENDIF
@@
 \RETURN  $N_{CA}$
-%\STATE $t \ += \delta t$
-%\ENDFOR
-%\ENDIF
-%\ENDIF
-%\ENDFOR
-%\end{enumerate}
+
 \end{algorithmic}
-%\caption{Algoritmo para obtener distribución de probabilidad de número de emisiones espontáneas}
+
 \end{algorithm}
@@
 \begin{center}
-\includegraphics[scale = 0.55]{newerrorppp.png}
+\includegraphics[scale = 0.55]{newerrorppp.pdf}
 \caption{\small{(a) Probability distributions for different mean number of spontaneous emissions $\mu$; (b) Calculation of variance with respect to the mean number of sponatenous emissions $\mu$.
@@
 \centering
-\includegraphics[scale = 0.45]{newsigmaeng.png}
+\includegraphics[scale = 0.45]{newsigmaeng.pdf}
 \caption{\small{Average number of spontaneous emissions $\pm \sigma$ with respect to cavity emissions, under parameters $\expval{n} \approx 1$, $\gamma = 1$ , $\kappa = g = 0.1$ and $\mathcal{E} =  \kappa |\langle n \rangle|[1 + 2g^2/\gamma \kappa]$.}}
@@
 
-\section{Correlation between atom and cavity emissions}
+\section{Correlation between photons emitted in different channels}\label{sc:correlation}
 So far we have obtained estimations for the number of spontaneous emission for each measured number of cavity emissions.
@@
 \begin{center}
-\includegraphics[scale = 0.45]{cor_2.png}
+\includegraphics[scale = 0.45]{million1.pdf}
 \caption{\small{Calculation of correlation using 500 time intervals, fixing $\expval{n} \approx 1$, $\gamma =$ 1.0, $g = $ 0.1, and with  $\mathcal{E} =  \kappa |\langle n \rangle|[1 + 2g^2/\gamma \kappa]$.}} \label{corrxy}
@@
 \begin{center}
-\includegraphics[scale = 0.45]{difftimes12.png}
+\includegraphics[scale = 0.45]{million2.pdf}
 \caption{\small{Correlation using different temporal intervals, fixing $\expval{n} \approx 1$, $\gamma =$ 1.0, $g =$ 0.1, and with  $\mathcal{E} =  \kappa |\langle n \rangle|[1 + 2g^2/\gamma \kappa]$.}}  \label{errorzz}
@@
 
-\section{Conclusions}
+\section{Conclusions}\label{sc:conclusions}
 In this work we considered a driven Jaynes-Cummings system.
@@
 
-Support by UNAM, projects CONACyT and UNAMPAPIIT IG100518.
+Support by UNAM, projects CONACyT and UNAM PAPIIT IG100518.
 

### 2019-11-14 paper1.2.1.tex
Muchos cambios de Pablo al texto. Falta conclusiones

@@
 $[\sigma_+, \sigma_-] = \sigma_z, \ [\sigma_\pm, \sigma_z] = \mp
-2\sigma_\pm$. The strength of the coupling between atom and cacity
+2\sigma_\pm$. The strength of the coupling between atom and cavity
 field is given by the constant
@@
 \begin{equation}
-H_{leak} = - i\hbar\kappa a^\dagger a\, .
+H_{leak} = - i\hbar\kappa a^\dagger a\, ,
 \end{equation}
@@
 We now summarize te quantum trajectory formalism \cite{bla} that we
-use to solve the system. We start with a state which represents a
-ground state of the atom with no photons in the cavity,
+use to solve the system. Each quantum trajectory is simulated as
+folllows. We start with a state which represents a ground state of the
+atom with no photons in the cavity,
 $\ket{\phi(t = 0)} = \ket{\downarrow} \times \ket{0}$, we evolve it
@@
 \end{equation}
-Using a non-hermitian Hamiltonian will have as a consequence that the
-probability won't be conserved \cite{Sakurai:1167961}. The evolution
-of the state through the schrödinger equation will be interrupted by a
-quantum jump – an abrupt change on our state in which a photoemission
-has ocurred. The probability for such quantum jump to happen will be
-given by the collapse probability
+The evolution of the state through the schrödinger equation will be
+interrupted by a quantum jump – an abrupt change on our state in which
+a photoemission has ocurred. The probability for such quantum jump to
+happen, during the time step $\delta t$, is given by the collapse
+probability
 \begin{equation} \label{probcol}
@@
 where
-\begin{eqnarray} \label{relprob}
-\delta p_1 &=& \gamma \bra{\phi (t)} \sigma_+
-               \sigma_-\ket{\psi (t)}\delta t \\
-  \delta p_2 &=& 2\kappa \bra{\phi (t)} a^\dagger a\ket{\psi (t)}\delta t 
+
+\begin{subequations}\label{relprob}
+  \begin{eqnarray}  \delta p_1 &=& \gamma \bra{\phi
+      (t)} \sigma_+
+                                                  \sigma_-\ket{\psi (t)}\delta t\, , \\
+    \delta p_2 &=& 2\kappa \bra{\phi (t)} a^\dagger a\ket{\psi
+                   (t)}\delta t \, .
   \end{eqnarray}
-We use these collapse probabilities to simulate the quantum
-trajectories, where we compare the collapse probability of eq.
-\eqref{probcol} with a random number $\epsilon$, uniformly distributed
-between zero and one. In the case the condition $\delta p > \epsilon$
-is fulfilled we simulate that a quantum jump has happened, by acting
-with one of the collapse operators. The operator with which we'll act
-on the state will be given according to the relative probabilities of
-eq. \eqref{relprob}.
+\end{subequations}
+We compare the collapse probability of Eq.~\eqref{probcol} with a
+random number $\epsilon$, uniformly distributed between zero and one.
+In the case the condition $\delta p > \epsilon$ is fulfilled we
+simulate that a quantum jump has happened, by acting with one of the
+collapse operators $a$ or $\sigma_-$ and renormalizating the obtained
+state. The operator that will act on the state will be given according
+to the relative probabilities of Eqs.~\eqref{relprob}.
 \begin{figure}[!t] 
@@
 \end{figure}
-Using equation \eqref{probcol} one can easily identify the
-corresponding collapse probabilities of the system. Having identified
-the collapse operators and the collapse probability, we simulate
-quantum trajectories, in which we keep count of the number of quantum
-jumps for each collapse operator, relating the number of quantum jumps
-associated to spontaneous emissions for each number of quantum jumps
-associated to cavity emissions until we reach a maximum number of
-cavity emissions, which we establish. The procedure of register of
-emissions is summarized in algorithm \ref{alg1}.
+If $\delta p > \epsilon$ is not fulfilled we just renormalize the
+state, because using a non-hermitian Hamiltonian will have as a
+consequence that the probability won't be conserved
+\cite{Sakurai:1167961}. For the next step we repeat the procedure
+using the resulting state for this step. One quantum trajectory of
+total time $t$ is obtained after repeating the previous procedure
+$t/\delta t$ steps. For each trajectory we count the number of quantum
+jumps, the jumps correponding to operator $a$ reduces the number of
+photons inside the cavity and corresponds to a photon that leak the
+cavity. The jumps corresponding to operator $\sigma_-$ interrumps its
+unitary evolution and send it back to the ground state, it corresponds
+to a spontaneous emission. The procedure to register emissions in the
+two different channels is summarized in algorithm \ref{alg1}.
 
-Realizing a large number of these trajectories, storing the registers
-in a matrix, where we keep track of the number of times that there
-were certain number of spontaneous emissions for each different number
-of cavity emission, enable us to obtain probability distributions that
-relate these two quantities.
+We realize a large number of these trajectories and keep track of the
+numbers of emission for each channel, with this data we can calculate
+probability distributions that relate these two quantities.
 
 \section{Counting photons emitted in different channels}\label{sc:distributions}
-In this section we use the quantum trajectory formalism to calculate
-the distribution probability of the number of spontaneous emissions by
-the atom conditioned to the number of photons that leaked the cavity
-from its mirror .
-\subsection{Probability distributions of emissions}
+In this section we calculate the probability distribution of the
+number of spontaneous emissions, $n_s$, under different conditions.
+First we calculate the distribution probability of $n_s$ when we know
+the number of leaked photons from the cavity, $n_c$; we use
+$p(n_s|n_c)$ to denote the distribution. Using this function we can
+investigate the correlation between $n_s$ and $n_c$ as a function of
+the cavity decay rate. This correlation is a measure of how much
+information we can obtain about $n_s$ if we know $n_c$.
 
-In Fig.\ref{probdiss} we see the probability of obtaining different number of spontaneous emissions for different number of cavity emissions.
-It is clear from the plot that our probability distributions are going to be more spread out as more time (and hence more cavity emissions) pass.
+The number of total photon emissions depends on how fast the atom is
+excited. In order to do a meaningful comparison when we change
+$\kappa$, we adjust the cavity drive so the mean number of photons
+inside the cavity is the same. If we keep $g$ constant this guarantees
+that the rate of atomic excitation is the same for different $\kappa$.
+
+In order to find the value of the cavity drive $\mathcal{E}$ as a
+function of the mean value of photons inside the cavity, we solve the
+Maxwell-Bloch equations. These equations give the dynamic of our
+system for the variables $\expval{a}, \expval{\sigma_-}$ and
+$\expval{\sigma_z}$ that correspond to the cavity field, atomic
+coherence, and atomic inversion respectively \cite{Alsing_1991}. For
+the case of the driven Jaynes-Cummings system, these equations are
+\begin{subequations} \label{maxbloch}
+\begin{equation} \label{bloch1}
+\dot{z} = (g/2)v + \mathcal{E} - \kappa z,
+\end{equation}
+\begin{equation} \label{bloch2}
+\dot{v} = gmz - (\gamma/2)v,
+\end{equation}
+\begin{equation} \label{bloch3}
+\dot{m} = -2g(z^*v + v^*z) - \gamma(m + 2),
+\end{equation}
+\end{subequations} 
+where we defined $z = e^{i\omega t}\expval{a}$,
+$v = 2e^{i\omega t}\expval{\sigma_-}$ and $m = 2\expval{\sigma_z}$.
+When the system is stable, we obtain, from
+\eqref{maxbloch}, the steady state
+solutions \cite{gagniuc2017markov}
+\begin{equation} \label{chaf1}
+\expval{a}_{ss} = \frac{\mathcal{E}e^{-i\omega t} +
+  g\expval{\sigma_-}_{ss}}{\kappa}\, ,
+\end{equation}
+\begin{equation} \label{chaf2}
+\expval{\sigma_-}_{ss} = -\frac{2g}{\gamma}\frac{\expval{a}_{ss}}{1 +
+  \frac{8g^2}{\gamma^2}|\expval{a}_{ss}|^2}\, ,
+\end{equation}
+\begin{equation}
+\bigg(\frac{\mathcal{E}}{\kappa}\bigg)^2 = |\expval{a}_{ss}|^2 \bigg(1
++ \frac{2g^2}{\gamma \kappa}\frac{1}{1 +
+  \frac{8g^2}{\gamma^2}|\expval{a}_{ss}|^2}\bigg)^2\, .
+\end{equation}
+When $\gamma \gg g$, the expected value of the number of photons in
+the cavity is 
+\begin{equation} \label{numfo}
+|\expval{a}_{ss}|^2 \approx \bigg(\frac{\mathcal{E}/\kappa}{1 + 2g^2/\gamma \kappa}\bigg)^2.
+\end{equation}
+
+\paragraph{The case when the number of photons leaked from the cavity  is known}
+\fxnote{No esta claro que hiciste aqui. Segun yo corriste el programa
+  distinto tiempo para cada caso}
+We calculate the distribution probability of the number of spontaneous
+emission conditioned to the number of photons detected leaking the
+cavity. We assume that the mean flux of photons in each channel is
+known in advance (they can be calculated knowing the cavity drive).
+The results are shown in Fig.\ref{probdiss}. As the number of leaked
+photons increases, the mean number of spontaneous emissions increases.
+This result is expected, because the number of leaked photons is
+correlated with the time we are counting spontaneus emission photons
+from a driven atom: the larger the number of leaked photons the larger
+the time we measure spontaneous emitted photons which implies a larger
+mean number of emitted photons. Also, the probability distribution is
+wider when the number of leaked photons increases, this implies less
+accuracy guessing the number of spontaneus emission as the number of
+leaked photons increases. If we know the cavity drive, this results
+does not imply that we can learn something extra about the number of
+spontaneous emissions knowing the number of photons leaked from the
+cavity; it is clear that when we increase the time window where we
+count photons, both, the number of leaked photons and the number of
+spontaneous emissions, increases.
+
+In section~\ref{sc:correlation} we will show
+when there is correlation between emissions in the two channels.
 
@@
 \end{center}
-\subsection{Extracting data from the probability distributions}
-Due to the complex dynamic of the driven Jaynes-Cummings system \cite{Carmichael1993Open}, it is important to know the dynamic that the system undergoes at the moment of obtaining the probability distributions, in order to have a better physical understanding of our results.
-In this case we opt for fixing the number of photons in the cavity.
+\paragraph{The case where the time we measure photons is fixed}
 
-We do this by solving what is known as the Maxwell-Bloch equations, which give the dynamic of our system for the variables  $\expval{a}, \expval{\sigma_-}$ and $\expval{\sigma_z}$ that correspond to the cavity field, atomic coherence, and atomic inversion respectively \cite{Alsing_1991}.
-For the case of the driven Jaynes-Cummings system, these equations are given by
-\begin{subequations} \label{maxbloch}
-\begin{equation} \label{bloch1}
-\dot{z} = (g/2)v + \mathcal{E} - \kappa z,
-\end{equation}
-\begin{equation} \label{bloch2}
-\dot{v} = gmz - (\gamma/2)v,
-\end{equation}
-\begin{equation} \label{bloch3}
-\dot{m} = -2g(z^*v + v^*z) - \gamma(m + 2),
-\end{equation}
-\end{subequations} 
-where we defined  $z = e^{i\omega t}\expval{a}$, $v = 2e^{i\omega t}\expval{\sigma_-}$ and $m = 2\expval{\sigma_z}$.
-Solving for the case in which our variables are constant we can obtain steady state solutions \cite{gagniuc2017markov}.
-From \eqref{bloch1} one can obtain the equation
-\begin{equation} \label{chaf1}
-\expval{a}_{ss} = \frac{\mathcal{E}e^{-i\omega t} + g\expval{\sigma_-}_{ss}}{\kappa}.
-\end{equation}
-While from \eqref{bloch2} and \eqref{bloch3} one obtains
-\begin{equation} \label{chaf2}
-\expval{\sigma_-}_{ss} = -\frac{2g}{\gamma}\frac{\expval{a}_{ss}}{1 + \frac{8g^2}{\gamma^2}|\expval{a}_{ss}|^2}.
-\end{equation}
-The requirement that both \eqref{chaf1} and \eqref{chaf2} are valid gives as result
-\begin{equation}
-\bigg(\frac{\mathcal{E}}{\kappa}\bigg)^2 = |\expval{a}_{ss}|^2 \bigg(1 + \frac{2g^2}{\gamma \kappa}\frac{1}{1 + \frac{8g^2}{\gamma^2}|\expval{a}_{ss}|^2}\bigg)^2.
-\end{equation}
-Considering $\gamma \gg g$, it is possible to clear $|\expval{a}|^2$, which allow us to obtain an expression for the expected value of the number of photons in the cavity
-\begin{equation} \label{numfo}
-|\expval{a}_{ss}|^2 = \bigg(\frac{\mathcal{E}/\kappa}{1 + 2g^2/\gamma \kappa}\bigg)^2.
-\end{equation}
+We know fix the time we measure photons, which is equivalente to
+fixing the mean number of spontaneous emited photons or the mean number
+of leaked photons from the cavity.
+
+We focus in the case where we fix the mean number of photons inside
+the cavity. This number depends on the cavity drive and the atomic
+parameters.
+
 \begin{figure}[!t]  
@@
 \section{Correlation between photons emitted in different channels}\label{sc:correlation}
-So far we have obtained estimations for the number of spontaneous emission for each measured number of cavity emissions.
-From our results it is obvious how the number of spontaneous emissions will increase with respect to the number of cavity emissions, given that more time will pass and more emissions will occur.
-One can also see how increasing the cavity linewidth $\kappa$ and keeping the other parameters constant will translate into a decrease of spontaneous emissions with respect to the number of cavity emissions.
-However, one question remains: is there a direct correlation between these two quantities?
-If yes, how this varies with respect to the cavity linewidth.
-From the beginning one could expect that in the case for a big $\kappa$ there would be no correlation at all, since this situation will be equivalent to the situation where there is no cavity.
+In this section we study the correlation between the number of
+spontaneus emission from the atom, $n_s$, and the number of photons
+that leak the cavity, $n_c$, as a function of the cavity decay rate,
+$\kappa$. We expect that when $\kappa\rightarrow\infty$ there would be
+no correlation between these two random variables, since this
+situation will be equivalent to the situation where there is no
+cavity.
 
-In order to have a measure of the correlation of the emissions we introduce the Pearson Correlation Coefficient \cite{benesty2009pearson}
+In order to have a measure of the correlation between emissions in the
+two different channels, we use the Pearson Correlation Coefficient
+\cite{benesty2009pearson}
 \begin{equation} 
-r_{xy} = \frac{\sum\limits_{i=1}^n(x_i - \bar{x})(y_i - \bar{y})}{\sqrt{\sum\limits_{i=1}^n(x_i - \bar{x})^2\sum\limits_{i=1}^n(y_i - \bar{y})^2}}.  \label{correlationc}
+r_{n_s,n_c} = \frac{\sum\limits_{i=1}^n(n_s^{(i)} -
+  \bar{n}_s)(n_c^{(i)} - \bar{n}_c)}{\sqrt{\sum\limits_{i=1}^n(n_s^{(i)}
+    - \bar{n}_s)^2\sum\limits_{i=1}^n(n_c^{(i)} - \bar{n}_c)^2}}\, ,  \label{correlationc}
 \end{equation}
-Having an equation that gives us a measure of the correlation, now we want the necessary data in order to obtain information about the correlation between the two types of emissions that we deal with.
-We can obtain this data by defining a temporal interval from which we make a register of the final number of spontaneous and cavity emissions.
-Given that what we are doing are essentially stochastic calculations, there will be variations in the final number of emissions for each trajectory.
-Making a large number of trajectories keeping track of the final number of emissions and pluggin the data in \eqref{correlationc} we are able to calculate the correlation.
+where $n^{(i)}$ is the output $i$ of the random variable $n$.
 
@@
 %kncrease or increases
-From Fig.
-\ref{corrxy} we see that, as we expected, the correlation goes to zero as we increase the cavity linewidth.
-Nonetheless, perhaps a more interesting question is: how high can this correlation be?
-Trying with values for $\kappa/\gamma$ lower than $0.1$, we notice that the correlation's increase stops and a decrease begins.
-It is possible that this stop in the increase of the correlation is due to the fact that if we keep decreasing the cavity linewidth it will come a point where the number of emissions will decrease considerably, diminishing the correlation.
-If this is the case we should expect that as we increase the temporal intervals, %the cavity linewidth at which the correlation starts decreasing should be smaller.
-we also see an increment of the correlation.
+
+The results are shown in Fig. \ref{corrxy}. We see a maximum
+correlation close to $0.1$ for $\kappa/\gamma\approx 0.05$ that
+decreases as $\kappa$ increases. From the figure it looks like the
+correlation goes to zero as $\kappa\rightarrow\infty$. With values for
+$\kappa/\gamma$ lower than $0.05$, we notice that the correlations
+increase stops and a decrease begins. This stop in the increase of the
+correlation is due to the fact that, as we keep decreasing the cavity
+linewidth the number of photons that leaks the cavity decreases
+considerably. In the limit where $\kappa=0$ the two random
+variables becomes independent, because the output of $n_c$ is zero
+with probability one. In this case there is no correlation between the two
+random variables.
+
+In Fig. \ref{errorzz} it is shown that as we increase the temporal
+interval where we count photons, we also see a small increment of the
+correlation, due to the fact that more photons leaks the cavity
+giving information about the system.
+\fxnote{Hay que mejorar las graficas. Las variables tienen que ser
+  mayores y las unidades estan mal}
 
@@
 
-In Fig.
-\ref{errorzz} we can appreciate that, as we increase the total temporal interval, there is also a slight increase in the correlation.
-This supports the idea that the time that takes for the system in stablishing the number photons will affect the value for the correlation, for values of $\kappa/\gamma$ lower than $0.1$.
+\section{Conclusions}\label{sc:conclusions}
+Differently to the case of an atom in free space, we can learn
+something about the number of spontaneus emissions done by an atom
+into different electromagnetic modes if the atom is inside a leaky
+cavity.
 
-\section{Conclusions}\label{sc:conclusions}
-In this work we considered a driven Jaynes-Cummings system.
-We made a program in which, through the use of quantum trajectory theory, we were able to obtain probability distributions that relate the number of spontaneous emissions given certain number of cavity emissions.
-Through the probability distributions we obtained estimations for the number of spontaneous emissions by measuring cavity emissions, considering the correspondent error.
-Finally we study the existing correlation where we saw how this correlation decreases as we increase the cavity linewidth.
-However, if we try with values for  $\kappa/\gamma < 0.1$, there comes a point where the increase stops and we see a decrease.
-We believe this is related to the fact that if we use enough small values of $\kappa$ there will come a point where the emission of photons will be too low and this will imply a decrease in the correlation.
-The results in this work provide a tool that could be useful in the manipulation of single photons product of spontaneous emission, and provide insight into the physical behavior of the driven Jaynes-Cummings model.
+In this work we considered a driven Jaynes-Cummings system. We made a
+program in which, through the use of quantum trajectory theory, we
+were able to obtain probability distributions that relate the number
+of spontaneous emissions given certain number of cavity emissions.
+Through the probability distributions we obtained estimations for the
+number of spontaneous emissions by measuring cavity emissions,
+considering the correspondent error. Finally we study the existing
+correlation where we saw how this correlation decreases as we increase
+the cavity linewidth. However, if we try with values for
+$\kappa/\gamma < 0.1$, there comes a point where the increase stops
+and we see a decrease. We believe this is related to the fact that if
+we use enough small values of $\kappa$ there will come a point where
+the emission of photons will be too low and this will imply a decrease
+in the correlation. The results in this work provide a tool that could
+be useful in the manipulation of single photons product of spontaneous
+emission, and provide insight into the physical behavior of the driven
+Jaynes-Cummings model.
 

### 2019-11-19 paper1.2.1.tex
Muchos cambios pablo

@@
     correspond to the emissions that leak through mirror
-    2.}} \label{probdisult}
+    2.}} 
 \end{center}
@@
 \section{Conclusions}\label{sc:conclusions}
-Differently to the case of an atom in free space, we can learn
-something about the number of spontaneus emissions done by an atom
-into different electromagnetic modes if the atom is inside a leaky
-cavity.
 
-In this work we considered a driven Jaynes-Cummings system. We made a
-program in which, through the use of quantum trajectory theory, we
-were able to obtain probability distributions that relate the number
-of spontaneous emissions given certain number of cavity emissions.
-Through the probability distributions we obtained estimations for the
-number of spontaneous emissions by measuring cavity emissions,
-considering the correspondent error. Finally we study the existing
-correlation where we saw how this correlation decreases as we increase
-the cavity linewidth. However, if we try with values for
-$\kappa/\gamma < 0.1$, there comes a point where the increase stops
-and we see a decrease. We believe this is related to the fact that if
-we use enough small values of $\kappa$ there will come a point where
-the emission of photons will be too low and this will imply a decrease
-in the correlation. The results in this work provide a tool that could
-be useful in the manipulation of single photons product of spontaneous
-emission, and provide insight into the physical behavior of the driven
-Jaynes-Cummings model.
+Atomic emission in cavity and non-cavity modes of an atom inside a
+leaky cavity are correlated. The correlations are produced because the
+cavity breaks the markovian behavior of atomic emission. the presence
+of correlation between photons measured in different directions is a
+signature of non-markovian behaviour. This correlation also allows us
+to improve the knowledge we know about the probability distribution of
+atomic spontaneus emission if we know the number of photons that leak
+the cavity.
+
+% In this work we considered a driven Jaynes-Cummings system. We made a
+% program in which, through the use of quantum trajectory theory, we
+% were able to obtain probability distributions that relate the number
+% of spontaneous emissions given certain number of cavity emissions.
+% Through the probability distributions we obtained estimations for the
+% number of spontaneous emissions by measuring cavity emissions,
+% considering the correspondent error. Finally we study the existing
+% correlation where we saw how this correlation decreases as we increase
+% the cavity linewidth. However, if we try with values for
+% $\kappa/\gamma < 0.1$, there comes a point where the increase stops
+% and we see a decrease. We believe this is related to the fact that if
+% we use enough small values of $\kappa$ there will come a point where
+% the emission of photons will be too low and this will imply a decrease
+% in the correlation. The results in this work provide a tool that could
+% be useful in the manipulation of single photons product of spontaneous
+% emission, and provide insight into the physical behavior of the driven
+% Jaynes-Cummings model.
+
+\fxnote{Creo que faltan dos cosas en este paper: la correlacion como
+  funcion de $g$ dado $\kappa$ constante. Una grafica mostrando, para
+  un tiempo fijo, como cambia la funcion de probabilidad para
+  emisiones espontaneas como funcion de fotones detectados fuera de la
+  cavida. Es decir: $p(n_s,n_c,t_0)$}
 

### 2019-11-30 newpaper.tex
Add files via upload

--- 2019-11-19 paper1.2.1.tex
@@
-\documentclass[conference]{IEEEtran}
-\IEEEoverridecommandlockouts
-% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
-\usepackage{cite}
-\usepackage{amsmath,amssymb,amsfonts}
-\usepackage{algorithmic}
-\usepackage{graphicx}
-\usepackage{textcomp}
-\usepackage{xcolor}
-\usepackage{amsfonts,amsmath, amssymb}
-%\usepackage[spanish]{babel}
-\usepackage{fancyhdr}
-%\usepackage[none]{hyphenat}
-\usepackage[nottoc, notlot, notlof]{tocbibind}
-\usepackage{cite}
-\usepackage{physics}
-\usepackage{bm}
-\usepackage[draft,inline,nomargin]{fixme} \fxsetup{theme=color}
-\usepackage{enumitem}
-\usepackage{a4wide}
-\usepackage{dsfont}
-\usepackage{ amssymb }
-\usepackage{cite}
-\usepackage[rightcaption]{sidecap}
-\usepackage{graphicx}
-\usepackage{algorithm}
-\usepackage{algorithmic}
-\usepackage{ragged2e}
-\usepackage{pdfpages} 
-\usepackage{csquotes}
-\usepackage{listings}
+% ****** Start of file apssamp.tex ******
+%
+%   This file is part of the APS files in the REVTeX 4.2 distribution.
+%   Version 4.2a of REVTeX, December 2014
+%
+%   Copyright (c) 2014 The American Physical Society.
+%
+%   See the REVTeX 4 README file for restrictions and more information.
+%
+% TeX'ing this file requires that you have AMS-LaTeX 2.0 installed
+% as well as the rest of the prerequisites for REVTeX 4.2
+%
+% See the REVTeX 4 README file
+% It also requires running BibTeX. The commands are as follows:
+%
+%  1)  latex apssamp.tex
+%  2)  bibtex apssamp
+%  3)  latex apssamp.tex
+%  4)  latex apssamp.tex
+%
+\documentclass[%
+ reprint,
+%superscriptaddress,
+%groupedaddress,
+%unsortedaddress,
+%runinaddress,
+%frontmatterverbose, 
+%preprint,
+%preprintnumbers,
+%nofootinbib,
+%nobibnotes,
+%bibnotes,
+ amsmath,amssymb,
+ aps, 
+%pra,
+%prb,
+%rmp,
+%prstab,
+%prstper,
+%floatfix,
+]{revtex4-2}
+
 \usepackage{hyperref}
@@
 }
-\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
-    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
+\usepackage[ruled,vlined]{algorithm2e}
+
+\usepackage{physics}
+\usepackage{fixme}
+%\usepackage{algorithm}
+\usepackage{algorithmic}
+\usepackage{graphicx}% Include figure files
+\usepackage{dcolumn}% Align table columns on decimal point
+\usepackage{bm}% bold math
+%\usepackage{hyperref}% add hypertext capabilities
+%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
+%\linenumbers\relax % Commence numbering lines
+
+%\usepackage[showframe,%Uncomment any one of the following lines to test 
+%%scale=0.7, marginratio={1:1, 2:3}, ignoreall,% default settings
+%%text={7in,10in},centering,
+%%margin=1.5in,
+%%total={6.5in,8.75in}, top=1.2in, left=0.9in, includefoot,
+%%height=10in,a5paper,hmargin={3cm,0.8in},
+%]{geometry}
+
 \begin{document}
 
-\title{Correlation between different emission channels from an atom inside a leaky driven cavity\\
-%{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
-%should not be used}
-\thanks{corresponding author e-mail: guillermopreisser@hotmail.com}
-}
+\preprint{APS/123-QED}
 
-\author{\IEEEauthorblockN{Guillermo Preisser and Pablo Barberis Blostein}
-\IEEEauthorblockA{\textit{Instituto de Investigaciones en Matemáticas Aplicadas y en Sistemas,
-} \\
-\textit{Universidad Nacional Autónoma de México, Ciudad Universitaria, 04510, CDMX, México.}\\
-Dated: 15 August, 2019}
-}
+\title{Correlation between different emission channels from an atom inside a leaky driven cavity}% Force line breaks with \\
 
-\maketitle
+\author{Guillermo Preisser}
+ \email{Corresponding author e-mail: guillermo.preisser@uabc.edu.mx}
+ %Lines break automatically or can be forced with \\
+\author{Pablo Barberis}%
+\affiliation{Instituto de Investigaciones en Matemáticas Aplicadas y en Sistemas, Universidad Nacional Autónoma de México, Ciudad Universitaria, 04510, CDMX, México.}
+
+\date{\today}% It is always \today, today,
+             %  but any date may be explicitly specified
 
@@
 
-%the recent advances?
-\section{Introduction}
+%\keywords{Suggested keywords}%Use showkeys class option if keyword
+                              %display desired
+\maketitle
+
+%\tableofcontents
+
+\section{INTRODUCTION}
+
 Spontaneous emission is a phenomenon that has been studied since the
@@
 the other modes (spontaneus emission), which are difficult to measure.
-\begin{center}
-\begin{figure*}\label{asa}
-\begin{center}
-\includegraphics[scale = 0.65]{newimagepaper.pdf}
-%\includegraphics[scale = 0.45]{image_paper222.png}
-\caption{\small{Physical arrangements of atom and atom in a cavity. In
-    both of these arrangements we consider a source which stimulates
-    the atom provoking it to spontaneously emit, once it decays. We
-    consider a detector in two directions, and we keep a register of
-    the number of photons measured in each direction. (a) In the case
-    for the atom we don't expect a correlation between m (the number
-    of photons measured in the upper side of the atom) and n (the
-    number of photons measured in the right side of the atom); (b) for
-    the atom in the cavity (a cavity with some loss rate) we study the
-    possibility that the cavity generates a correlation between the
-    emissions of the atom and the emissions of the cavity, which
-    correspond to the emissions that leak through mirror
-    2.}} 
-\end{center}
-\end{figure*}
-\end{center}
 
@@
 Concluding remarks are given in section \ref{sc:conclusions}
+\begin{center}
+\begin{figure*}\label{asa}
+\begin{center}
+\includegraphics[scale = 0.65]{newimagepaper.pdf}
+%\includegraphics[scale = 0.45]{image_paper222.png}
+\caption{\small{Physical arrangements of atom and atom in a cavity. In
+    both of these arrangements we consider a source which stimulates
+    the atom provoking it to spontaneously emit, once it decays. We
+    consider a detector in two directions, and we keep a register of
+    the number of photons measured in each direction. (a) In the case
+    for the atom we don't expect a correlation between m (the number
+    of photons measured in the upper side of the atom) and n (the
+    number of photons measured in the right side of the atom); (b) for
+    the atom in the cavity (a cavity with some loss rate) we study the
+    possibility that the cavity generates a correlation between the
+    emissions of the atom and the emissions of the cavity, which
+    correspond to the emissions that leak through mirror
+    2.}} 
+\end{center}
+\end{figure*}
+\end{center}
 
 \section{Driven Jaynes-Cummings model}\label{sc:drivenjc}
-We consider a system consisting of a two-level atom, coupled to a mode
+e consider a system consisting of a two-level atom, coupled to a mode
 of a leaky cavity. The mode is driven by a coherent field resonant
@@
 \end{subequations}
+\makeatletter
+%\DeclareCaptionLabelFormat{numberless}{\ALG@name#1}
+%\captionsetup[algorithm]{labelformat=numberless} 
+\makeatother
+\begin{algorithm}
+\caption{Pseudocode for register of cavity losses and atom's spontaneous emissions}
+\label{alg1}
+\begin{algorithmic}
+%\caption{Pseudocode for register of cavity losses and atom's spontaneous emissions}
+\STATE $N$: number of temporal intervals
+\STATE $N_A $: number of spontaneous emissions
+\STATE $N_C$: number of cavity emissions
+\STATE $N_{max}$: maximum number of cavity emissions
+\STATE $N_{CA}$: matrix relating the number of cavity emissions with the number of spontaneous emissions
+
+\STATE
+\STATE Initial conditions:
+\STATE $N_A = 0; N_C = 0;$
+\STATE $N_{CA} = \text{zeros}(N_{max},2);  k = 0;$
+
+\STATE
+
+\FOR{$i = 1$ to N} 
+\STATE $\ket{ \phi^1(t + \delta t)} = e^{-iH\delta t/\hbar}\ket{\phi (t)}$
+\STATE$ \delta p_1 = \delta t\bra{\phi(t)}C^\dagger_1 C_1\ket{\phi(t)}$
+\STATE $ \delta p_2 =  \delta t\bra{\phi(t)}C^\dagger_2 C_2\ket{\phi(t)}$
+\STATE $\delta p = \delta p_1 + \delta p_2$
+\IF {$\delta p > \epsilon$}
+\IF{$ \tfrac{\delta p_1}{\delta p} > \epsilon$}
+\STATE $\ket{\phi (t + \delta t)} = \frac{C_1 \ket{ \ \phi(t)}}{\sqrt \frac{\delta p_1}{\delta t}}$
+\STATE $N_A = N_A + 1$
+\ELSE
+\STATE $\ket{\phi (t + \delta t)} = \frac{C_2 \ket{ \ \phi(t)}}{\sqrt \frac{\delta p_2}{\delta t}}$
+\STATE $N_C = N_C + 1$
+\STATE $N_{CA}[k+1,1] = N_C$
+\STATE  $N_{CA}[k+1,2] = N_A$
+\STATE $k = k+1$
+\IF{$N_C == N_{max}$}
+\STATE \textbf{\textit{break}}
+\ENDIF
+
+\ENDIF
+\ELSE
+\STATE $\ket{ \phi(t + \delta t)} = \frac{\ket{\phi^1 (t+ \delta t)}}{\sqrt{1-\delta p}}$
+\STATE $t \ += \delta t$
+\ENDIF
+\ENDFOR
+\RETURN  $N_{CA}$
+\end{algorithmic}
+\end{algorithm}
 We compare the collapse probability of Eq.~\eqref{probcol} with a
@@
 to a spontaneous emission. The procedure to register emissions in the
-two different channels is summarized in algorithm \ref{alg1}.
+two different channels is summarized in algorithm. \ref{alg1}.
 
@@
 solutions \cite{gagniuc2017markov}
+\begin{center}
+\begin{figure*}[!t]\label{error2}
+\begin{center}
+\includegraphics[scale = 0.7]{newerrorppp.pdf}
+\caption{\small{(a) Probability distributions for different mean number of spontaneous emissions $\mu$; (b) Calculation of variance with respect to the mean number of sponatenous emissions $\mu$.
+In both cases we consider $\expval{n} \approx 1$, $\gamma = 1.0$ , $\kappa = g = 0.1$ and $\mathcal{E} =  \kappa |\langle n \rangle|[1 + 2g^2/\gamma \kappa]$.}} \label{probdisult}
+\end{center}
+\end{figure*}
+\end{center}
 \begin{equation} \label{chaf1}
@@
 
-\begin{algorithm}[!t]
-\caption{Pseudocode for register of cavity losses and atom's spontaneous emissions}
-\label{alg1}
-\begin{algorithmic}
-\STATE $N$: number of temporal intervals
-\STATE $N_A $: number of spontaneous emissions
-\STATE $N_C$: number of cavity emissions
-\STATE $N_{max}$: maximum number of cavity emissions
-\STATE $N_{CA}$: matrix relating the number of cavity emissions with the number of spontaneous emissions
-%\STATE $K [\equiv] contador$
+\begin{figure}[!b]  
+\centering
+\includegraphics[scale = 0.5]{newsigmaengg.pdf}
+\caption{\small{Average number of spontaneous emissions $\pm \sigma$ with respect to cavity emissions, under parameters $\expval{n} \approx 1$, $\gamma = 1$ , $\kappa = g = 0.1$ and $\mathcal{E} =  \kappa |\langle n \rangle|[1 + 2g^2/\gamma \kappa]$.}}
+\label{graph}
+\end{figure}
 
-\STATE
-\STATE Initial conditions:
-\STATE $N_A = 0; N_C = 0;$
-\STATE $N_{CA} = \text{zeros}(N_{max},2);  k = 0;$
-
-\STATE
-
-\FOR{$i = 1$ to N} 
-\STATE $\ket{ \phi^1(t + \delta t)} = e^{-iH\delta t/\hbar}\ket{\phi (t)}$
-\STATE$ \delta p_1 = \delta t\bra{\phi(t)}C^\dagger_1 C_1\ket{\phi(t)}$
-\STATE $ \delta p_2 =  \delta t\bra{\phi(t)}C^\dagger_2 C_2\ket{\phi(t)}$
-\STATE $\delta p = \delta p_1 + \delta p_2$
-\IF {$\delta p > \epsilon$}
-\IF{$ \tfrac{\delta p_1}{\delta p} > \epsilon$}
-\STATE $\ket{\phi (t + \delta t)} = \frac{C_1 \ket{ \ \phi(t)}}{\sqrt \frac{\delta p_1}{\delta t}}$
-\STATE $N_A = N_A + 1$
-\ELSE
-\STATE $\ket{\phi (t + \delta t)} = \frac{C_2 \ket{ \ \phi(t)}}{\sqrt \frac{\delta p_2}{\delta t}}$
-\STATE $N_C = N_C + 1$
-\STATE $N_{CA}[k+1,1] = N_C$
-\STATE  $N_{CA}[k+1,2] = N_A$
-\STATE $k = k+1$
-\IF{$N_C == N_{max}$}
-\STATE \textbf{\textit{break}}
-\ENDIF
-
-\ENDIF
-\ELSE
-\STATE $\ket{ \phi(t + \delta t)} = \frac{\ket{\phi^1 (t+ \delta t)}}{\sqrt{1-\delta p}}$
-\STATE $t \ += \delta t$
-\ENDIF
-\ENDFOR
-\RETURN  $N_{CA}$
-
-\end{algorithmic}
-
-\end{algorithm}
-
-\begin{center}
-\begin{figure*}[!t]\label{error2}
-\begin{center}
-\includegraphics[scale = 0.55]{newerrorppp.pdf}
-\caption{\small{(a) Probability distributions for different mean number of spontaneous emissions $\mu$; (b) Calculation of variance with respect to the mean number of sponatenous emissions $\mu$.
-In both cases we consider $\expval{n} \approx 1$, $\gamma = 1.0$ , $\kappa = g = 0.1$ and $\mathcal{E} =  \kappa |\langle n \rangle|[1 + 2g^2/\gamma \kappa]$.}} \label{probdisult}
-\end{center}
-\end{figure*}
-\end{center}
 \paragraph{The case where the time we measure photons is fixed}
@@
 
-\begin{figure}[!t]  
-\centering
-\includegraphics[scale = 0.45]{newsigmaeng.pdf}
-\caption{\small{Average number of spontaneous emissions $\pm \sigma$ with respect to cavity emissions, under parameters $\expval{n} \approx 1$, $\gamma = 1$ , $\kappa = g = 0.1$ and $\mathcal{E} =  \kappa |\langle n \rangle|[1 + 2g^2/\gamma \kappa]$.}}
-\label{graph}
-\end{figure} 
 Having Eq.
@@
 \begin{center}
-\includegraphics[scale = 0.45]{million1.pdf}
+\includegraphics[scale = 0.5]{million1.pdf}
 \caption{\small{Calculation of correlation using 500 time intervals, fixing $\expval{n} \approx 1$, $\gamma =$ 1.0, $g = $ 0.1, and with  $\mathcal{E} =  \kappa |\langle n \rangle|[1 + 2g^2/\gamma \kappa]$.}} \label{corrxy}
@@
 \begin{center}
-\includegraphics[scale = 0.45]{million2.pdf}
+\includegraphics[scale = 0.5]{million2.pdf}
 \caption{\small{Correlation using different temporal intervals, fixing $\expval{n} \approx 1$, $\gamma =$ 1.0, $g =$ 0.1, and with  $\mathcal{E} =  \kappa |\langle n \rangle|[1 + 2g^2/\gamma \kappa]$.}}  \label{errorzz}
@@
 %kncrease or increases
+
+\begin{center}
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[scale = 0.5]{ccorr1.pdf}
+\caption{\small{Mean value of spontaneous emissions after post-selection, fixing $\expval{n} \approx 1$, $\gamma =$ 1.0, $g = \kappa =$ 0.1, and with  $\mathcal{E} =  \kappa |\langle n \rangle|[1 + 2g^2/\gamma \kappa]$.}}  \label{errorzz}
+\end{center}
+\end{figure}
+\end{center}
+
+\begin{center}
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[scale = 0.5]{cnocorr1.pdf}
+\caption{\small{Mean value of spontaneous emissions after post-selection, fixing $\expval{n} \approx 1$, $\gamma = \kappa =$ 1.0, $g =$ 0.1, and with  $\mathcal{E} =  \kappa |\langle n \rangle|[1 + 2g^2/\gamma \kappa]$.}}  \label{errorzz}
+\end{center}
+\end{figure}
+\end{center}
 
@@
 \section{Conclusions}\label{sc:conclusions}
-
 Atomic emission in cavity and non-cavity modes of an atom inside a
@@
 
-\section*{Acknowledgment}
+\bibliography{reftesis}% Produces the bibliography via BibTeX.
 
-Support by UNAM, projects CONACyT and UNAM PAPIIT IG100518.
-
-\bibliographystyle{IEEEtran}
-\bibliography{reftesis}
 \end{document}
+%
+% ****** End of file apssamp.tex ******

### 2019-12-02 newpaper.tex
Add files via upload

@@
 \includegraphics[scale = 0.5]{million1.pdf}
-\caption{\small{Calculation of correlation using 500 time intervals, fixing $\expval{n} \approx 1$, $\gamma =$ 1.0, $g = $ 0.1, and with  $\mathcal{E} =  \kappa |\langle n \rangle|[1 + 2g^2/\gamma \kappa]$.}} \label{corrxy}
+\caption{\small{Calculation of correlation using a time interval, tf = 500, fixing $\expval{n} \approx 1$, $\gamma =$ 1.0, $g = $ 0.1, and with  $\mathcal{E} =  \kappa |\langle n \rangle|[1 + 2g^2/\gamma \kappa]$.}} \label{corrxy}
 \end{center}  
@@
 
-\begin{center}
-\begin{figure}[h!]
-\begin{center}
-\includegraphics[scale = 0.5]{ccorr1.pdf}
-\caption{\small{Mean value of spontaneous emissions after post-selection, fixing $\expval{n} \approx 1$, $\gamma =$ 1.0, $g = \kappa =$ 0.1, and with  $\mathcal{E} =  \kappa |\langle n \rangle|[1 + 2g^2/\gamma \kappa]$.}}  \label{errorzz}
-\end{center}
-\end{figure}
-\end{center}
+%\begin{center}
+%\begin{figure}[h!]
+%\begin{center}
+%\includegraphics[scale = 0.7]{lastgraph.pdf}
+%\caption{\small{Mean value of spontaneous emissions after post-selection, fixing $\expval{n} \approx 1$, $\gamma =$ 1.0, $g = \kappa =$ 0.1, and with  $\mathcal{E} =  \kappa |\langle n \rangle|[1 + 2g^2/\gamma \kappa]$.}}  \label{errorzz}
+%\end{center}
+%\end{figure}
+%\end{center}
 
 \begin{center}
-\begin{figure}[h!]
+\begin{figure*}[!t]\label{error2}
 \begin{center}
-\includegraphics[scale = 0.5]{cnocorr1.pdf}
-\caption{\small{Mean value of spontaneous emissions after post-selection, fixing $\expval{n} \approx 1$, $\gamma = \kappa =$ 1.0, $g =$ 0.1, and with  $\mathcal{E} =  \kappa |\langle n \rangle|[1 + 2g^2/\gamma \kappa]$.}}  \label{errorzz}
+\includegraphics[scale = 0.7]{lastgraph.pdf}
+\caption{\small{Mean value of spontaneous emissions after post-selection, fixing $\expval{n} \approx 1$, $\gamma =$ 1.0, $g = $ 0.1, and with  $\mathcal{E} =  \kappa |\langle n \rangle|[1 + 2g^2/\gamma \kappa]$ and with tf = 500.
+(a) We consider $\kappa = $0.1 which has a correlation value around $0.1$; (b) we consider $\kappa = $1.0, which has a correlation value around $0.01$.}} \label{probdisult}
 \end{center}
-\end{figure}
+\end{figure*}
 \end{center}
-
 The results are shown in Fig. \ref{corrxy}. We see a maximum

### 2019-12-09 newpaper.tex
Add files via upload

@@
 \begin{center}
-\begin{figure*}[!t]\label{error2}
+\begin{figure*}[!t]
 \begin{center}
-\includegraphics[scale = 0.7]{lastgraph.pdf}
+\includegraphics[scale = 0.7]{lastgraph1.pdf}
 \caption{\small{Mean value of spontaneous emissions after post-selection, fixing $\expval{n} \approx 1$, $\gamma =$ 1.0, $g = $ 0.1, and with  $\mathcal{E} =  \kappa |\langle n \rangle|[1 + 2g^2/\gamma \kappa]$ and with tf = 500.
-(a) We consider $\kappa = $0.1 which has a correlation value around $0.1$; (b) we consider $\kappa = $1.0, which has a correlation value around $0.01$.}} \label{probdisult}
+(a) We consider $\kappa = $0.05 which has a correlation value around $0.1$; (b) we consider $\kappa = $1.0, which has a correlation value around $0.01$.}} \label{probdisult}
 \end{center}
@@
 This supports the idea that the time that takes for the system in stablishing the number photons will affect the minimum value of cavity linewidth at which the correlation starts decreasing.
+Studying this correlation further, we see how the average number of
+spontaneous emissions varies given the number of cavity emissions during a constant length of time. Making a 
+post-selection around the average number of cavity emissions we make a gaussian
+adjustment for the average number of spontaneous emissions and the corresponding 
+standard deviation. Such results are shown in Fig. \ref{probdisult}, where we notice that
+for the case in which we have a correlation around $0.1$, making a post-selection with a 
+bigger number of cavity emissions turns into an increase of the mean number of spontaneous emissions,
+ while the opposite happens for a lower number of cavity emissions. On the other hand, when 
+the correlation is around $0.01$, the change in the average number of spontaneous emissions
+after the post-selection is barely noticeable.
 

### 2019-12-17 newpaper.tex
algunos cambios de pablo

@@
 %floatfix,
-]{revtex4-2}
+]{revtex4-1}
 
@@
 \usepackage{physics}
-\usepackage{fixme}
+\usepackage[draft,inline,nomargin]{fixme} \fxsetup{theme=color}
 %\usepackage{algorithm}
@@
 
-\section{INTRODUCTION}
+\section{Introduction}
 
@@
 early XX century \cite{10.2307/94746, 1917PhyZ...18..121E}. One of the
-main characteristics of spontaneous emission is that
-\fxnote{spontaneus emission no es exponencial, es aproximadamente
-  exponencial, si quitas la aproximacion markoviana te queda una cola
-  polinomial, quite la oracion} the exact time of emission, as well as
-the direction in which the photon is emitted, is random, which
-difficults its measurement. On the other hand, photons emitted from a
-cavity are easy to measure, partly due the fact that we know that they
-leave the cavity through one of the lateral mirrors \cite{326305,
-  doi:10.1063/1.113345}. The randomness of the direction in which the
-photons are emitted by atoms in free space difficults photon counting
-experiments. To sort out this difficulty one could think of a physical
-arrangement, in which the two-level atom is coupled to the stimulated
-mode of a cavity, as it is shown in Fig. \ref{asa} (b). In this
-physical arrangement, \fxnote*{tienes una cita donde lo nombren
-  asi?}{which is known as the driven Jaynes-Cummings model}, one could
-try to estimate the number of spontaneous emissions of the atom
---which are emitted in modes that are not cavity modes and therefore
-escape the cavity-- by measuring the photons that leak through one of
-the cavity mirrors. In the case that a
-correlation exists between the two quantities, we can count the number
-of photons that leak the cavity through its mirror, which is easy to
-measure, to find information about the number of photons emitted into
-the other modes (spontaneus emission), which are difficult to measure.
+main characteristics of spontaneous emission is that the exact time of
+emission, as well as the direction in which the photon is emitted, is
+random, which difficults its measurement. On the other hand, photons
+emitted from a cavity mirror are easier to measure because we know
+their direction \cite{326305, doi:10.1063/1.113345}. The randomness of
+the direction in which the photons are emitted by atoms in free space
+difficults photon counting experiments. To sort out this difficulty
+one could think of a physical arrangement in which a two-level atom is
+coupled to a driven cavity, as it is shown in Fig. \ref{asa}. In this
+physical arrangement, one could try to estimate the number of
+spontaneous emissions of the atom --which are emitted in modes that
+are not cavity modes and therefore escape the cavity to its side-- by
+measuring the photons that leak through one of the cavity mirrors. In
+the case that a correlation exists between the two quantities, we can
+count the number of photons that leak the cavity through its mirror,
+which is easy to measure, to find information about the number of
+photons emitted into the other modes (spontaneus emission), which are
+difficult to measure.
 
 In the case of a two-level atom in free space, the absence of
-correlation between different channels is the result of the markovian
-approximation, which assumes that the environment has no memory of
-previous interactions with the system \cite{daley2014quantum}. Two
-atomic emissions would be correlated if one of the emissions stay
-registered in the environment and, somehow, influence the second
-emission of a two-level atom at a later time; the Markovian
-approximation does not allow memory effects and there is no
-correlation between the number of emissions of each source: knowing
-the number of photons emitted in some region of the space during some
-time does not give me any information on the number of photons emitted
-in other region of the space. Nevertheless, for the case of an atom
-inside a cavity, before a photon leaks the cavity, it will interact
-with the atom for some time. This interaction with the atom before the
-emission generates a correlation between photons that leak the cavity
-through its mirror and photons that leak the cavity through its side.
+correlation between photons emitted in different directions is due to
+the fact that the atom's environment memory of previous interactions
+with it, is very short; this is what justify the markovian
+approximation \cite{daley2014quantum}. Two atomic emissions would be
+correlated if one of the emissions stay registered in the environment
+and, somehow, influence the second emission.
 
-We use quantum trajectory theory to theoretically calculate the
-correlation between different emission channels. A quantum trajectory
-is the description of a continuously monitored quantum system
-conditioned on a particular past history of coherent evolution and
-collapse \cite{Carmichael1993Open}. These trajectories are simulated
-through a stochastic process, which define the times when the
-collapses occur. Each trajectory gives us the number of photon emitted
-in each channel. Simulating a large number of trajectories and
-registering the number of photon emissions into the two channels, we
-obtain its correlation. The correlation varies with the cavity
-linewidth and the atom-cavity coupling. For a very bad cavity we
-recover the free space result: there is no correlation between the two
-channels.
+For an atom in free space, knowing the number of photons emitted in
+some region of the space during some time does not give any
+information on the number of photons emitted in other region of the
+space. Nevertheless, for the case of an atom inside a cavity, before a
+photon, emitted from the atom into the cavity mode, leaks the cavity,
+it will interact with the atom for some time. This interaction creates
+a correlation between photons that leak the cavity through its mirror
+and photons that are emitted from the atom to the cavity side
+(spontaneus emissions).
 
-This article is organized as follows: A general overview of the driven
-Jaynes-Cummings model is presented in section \ref{sc:drivenjc}. In
-section \ref{sc:distributions} we obtain probability distributions
-that relate the number of spontaneous and cavity emissions. In section
-\ref{sc:correlation} we calculate the correlation between the two variables.
-Concluding remarks are given in section \ref{sc:conclusions}
+We use quantum trajectories theory to calculate the correlation between
+different emission channels. A quantum trajectory is the description
+of a continuously monitored quantum system conditioned on a particular
+past history of coherent evolution and collapse
+\cite{Carmichael1993Open}. These trajectories are simulated through a
+stochastic process, which define the times when the collapses occur.
+Each trajectory gives us the number of photon emitted in each channel.
+Simulating a large number of trajectories and registering the number
+of photon emissions into the two channels, we obtain its correlation.
+The correlation varies with the cavity linewidth and the atom-cavity
+coupling. For a very bad cavity we recover the free space result:
+there is no correlation between the two channels.
+
+This article is organized as follows: A general overview of the
+theoretical model is presented in section \ref{sc:drivenjc}. In
+section \ref{sc:distributions} we obtain join probability distribution
+of the the number of spontaneous and cavity emissions. In section
+\ref{sc:correlation} we calculate the correlation between the two
+variables. Concluding remarks are given in section
+\ref{sc:conclusions}
 \begin{center}
@@
 %\includegraphics[scale = 0.45]{image_paper222.png}
-\caption{\small{Physical arrangements of atom and atom in a cavity. In
-    both of these arrangements we consider a source which stimulates
-    the atom provoking it to spontaneously emit, once it decays. We
-    consider a detector in two directions, and we keep a register of
-    the number of photons measured in each direction. (a) In the case
-    for the atom we don't expect a correlation between m (the number
-    of photons measured in the upper side of the atom) and n (the
-    number of photons measured in the right side of the atom); (b) for
-    the atom in the cavity (a cavity with some loss rate) we study the
-    possibility that the cavity generates a correlation between the
-    emissions of the atom and the emissions of the cavity, which
-    correspond to the emissions that leak through mirror
-    2.}} 
+\caption{A driven atom in free space (a) and inside a driven leaky
+  cavity (b). Each time the atom decays, it emits a photon. In each
+  case, we count the number of photons $m$ and $n$, emitted in two
+  different directions respectively. For the atom in free space there
+  is no correlation between $m$ and $n$. For the atom inside the leaky
+  cavity we find a correlation between $m$ and $n$.}
 \end{center}
@@
 
-\section{Driven Jaynes-Cummings model}\label{sc:drivenjc}
-e consider a system consisting of a two-level atom, coupled to a mode
+\section{Theoretical model}\label{sc:drivenjc}
+We consider a system consisting of a two-level atom, coupled to a mode
 of a leaky cavity. The mode is driven by a coherent field resonant

### 2019-12-17 newpaper.tex
Cambios de pablo al texto

@@
 \caption{A driven atom in free space (a) and inside a driven leaky
-  cavity (b). Each time the atom decays, it emits a photon. In each
-  case, we count the number of photons $m$ and $n$, emitted in two
-  different directions respectively. For the atom in free space there
-  is no correlation between $m$ and $n$. For the atom inside the leaky
-  cavity we find a correlation between $m$ and $n$.}
+  cavity (b). We count the number of photons $m$ and $n$, emitted by
+  the atom in two different directions. For the atom in free space
+  there is no correlation between $m$ and $n$. For the atom inside the
+  leaky cavity we find a correlation between $m$ and $n$.}
 \end{center}
@@
 \includegraphics[scale = 0.5]{distributioneng.pdf}
-\caption{\small{Probability distribution of spontaneous emissions for different number of cavity losses in a driven Jaynes-cummings model, doing $100,000$ quantum trajectory simulations, with parameters $\mathcal{E}  = \kappa = \gamma = g = 1$.}} \label{probdiss}
+\caption{Probability distribution of spontaneous emissions for
+  different number of cavity photons. Parameters $\mathcal{E}  =
+  \kappa = \gamma = g = 1$, $100,000$ quantum trajectories. } \label{probdiss}
 \end{figure}
@@
 In this section we calculate the probability distribution of the
-number of spontaneous emissions, $n_s$, under different conditions.
-First we calculate the distribution probability of $n_s$ when we know
-the number of leaked photons from the cavity, $n_c$; we use
-$p(n_s|n_c)$ to denote the distribution. Using this function we can
-investigate the correlation between $n_s$ and $n_c$ as a function of
-the cavity decay rate. This correlation is a measure of how much
-information we can obtain about $n_s$ if we know $n_c$.
+number of spontaneous emissions $n_s$, under two different conditions.
+First, we study the distribution probability of $n_s$ when we consider
+the set of quantum trajectories where the number of leaked photons
+from the cavity is $n_c$. This simulate the physical situation where
+we count the number of spontaneus photons until the moment where the
+number of leaked photons from the cavity is $n_c$. It is impossible to
+know in advance how long it takes to the cavity to leak $n_c$ photons,
+thus the time each quantum trajectory is evolved is not fixed. Second,
+we fix the time each quantum trajectory is evolved and count the
+number of spontaneus emissions $n_s$, and cavity emissions $n_c$. From
+the set of quantum trajectories evolved a fixed time, we calculate the
+joint probability $p(n_s,n_c)$, of finding $n_s$ spontaneous emissions
+and $n_c$ cavity emissions. Using $p(n_s,n_c)$ we calculate the
+correlations between the two random variables. This correlation is a
+measure of how much information we can obtain about $n_s$ if we know
+$n_c$.
 
@@
 solutions \cite{gagniuc2017markov}
-\begin{center}
-\begin{figure*}[!t]\label{error2}
-\begin{center}
-\includegraphics[scale = 0.7]{newerrorppp.pdf}
-\caption{\small{(a) Probability distributions for different mean number of spontaneous emissions $\mu$; (b) Calculation of variance with respect to the mean number of sponatenous emissions $\mu$.
-In both cases we consider $\expval{n} \approx 1$, $\gamma = 1.0$ , $\kappa = g = 0.1$ and $\mathcal{E} =  \kappa |\langle n \rangle|[1 + 2g^2/\gamma \kappa]$.}} \label{probdisult}
-\end{center}
-\end{figure*}
-\end{center}
+
 \begin{equation} \label{chaf1}
@@
 
-\paragraph{The case when the number of photons leaked from the cavity  is known}
-\fxnote{No esta claro que hiciste aqui. Segun yo corriste el programa
-  distinto tiempo para cada caso}
+\subsection{Quantum trajectories with fixed number of photons leaked from the cavity}
 We calculate the distribution probability of the number of spontaneous
-emission conditioned to the number of photons detected leaking the
-cavity. We assume that the mean flux of photons in each channel is
-known in advance (they can be calculated knowing the cavity drive).
-The results are shown in Fig.\ref{probdiss}. As the number of leaked
+emission when a fixed number of photons leaked the cavity. We assume
+that the mean number of photons inside the cavity is $1/9$. The
+results are shown in Fig.~\ref{probdiss}. As the number of leaked
 photons increases, the mean number of spontaneous emissions increases.
@@
 from a driven atom: the larger the number of leaked photons the larger
-the time we measure spontaneous emitted photons which implies a larger
-mean number of emitted photons. Also, the probability distribution is
-wider when the number of leaked photons increases, this implies less
-accuracy guessing the number of spontaneus emission as the number of
-leaked photons increases. If we know the cavity drive, this results
-does not imply that we can learn something extra about the number of
-spontaneous emissions knowing the number of photons leaked from the
-cavity; it is clear that when we increase the time window where we
-count photons, both, the number of leaked photons and the number of
-spontaneous emissions, increases.
+the time we measure spontaneous emitted photons, which implies a
+larger mean number of emitted photons. Also, as shown in
+Fig~\ref{graph}, the probability distribution is wider as the number
+of leaked photons increases, this implies less accuracy guessing the
+number of spontaneus emission. If we know the cavity drive, this
+results does not imply that we can learn something extra about the
+number of spontaneous emissions knowing the number of photons leaked
+from the cavity; it is clear that when we increase the time window
+where we count photons, both, the number of leaked photons and the
+number of spontaneous emissions, increases.
 
@@
 
-\begin{figure}[!b]  
+\begin{figure}[!h]  
 \centering
-\includegraphics[scale = 0.5]{newsigmaengg.pdf}
-\caption{\small{Average number of spontaneous emissions $\pm \sigma$ with respect to cavity emissions, under parameters $\expval{n} \approx 1$, $\gamma = 1$ , $\kappa = g = 0.1$ and $\mathcal{E} =  \kappa |\langle n \rangle|[1 + 2g^2/\gamma \kappa]$.}}
+\includegraphics[scale = 0.5]{newsigmaeng.pdf}
+\caption{Average number of spontaneous emissions $\pm \sigma$ with respect to cavity emissions, under parameters $\expval{n} \approx 1$, $\gamma = 1$ , $\kappa = g = 0.1$ and $\mathcal{E} =  \kappa |\langle n \rangle|[1 + 2g^2/\gamma \kappa]$.}
 \label{graph}
@@
 
-\paragraph{The case where the time we measure photons is fixed}
+\subsection{Quantum trajectories with fixed duration}
+We consider the set of quantum trajectories of the same duration. This
+corresponds to fixing the time we measure photons. Each set of quantum
+trajectories with the same duration is labelled with its mean number
+of spontaneous emitted photons $\mu$. We consider the case where we
+fix the mean number of photons inside the cavity to $1$. As shown by
+Eq.~(\ref{numfo}), this number depends on the drive, and cavity and
+atomic parameters.
 
-We know fix the time we measure photons, which is equivalente to
-fixing the mean number of spontaneous emited photons or the mean number
-of leaked photons from the cavity.
+In Fig.~\ref{error2}(a) the probability distribution of spontaneous
+emitted photons is shown for different mean values. As it is shown in
+Fig.~\ref{error2}(b), the width of the distribution increases linearly
+with the mean number of spontaneus emission. This behaviour does not
+imply any correlation between the number of spontaneus emissions and
+cavity emissions.
 
-We focus in the case where we fix the mean number of photons inside
-the cavity. This number depends on the cavity drive and the atomic
-parameters.
+Now we focus in the case, where given a set of quantum trajectories
+with fixed duration, we postselect all the trajectories where the
+number of cavity emissions is a fixed number $n_c$, and plot
+$p(n_s|n_c)$, the probability distribution of the number of spontaneus
+emissions $n_s$, under the condition that $n_c$ cavity emissions
+happened. If $p(n_s|n_c)\neq p(n_s)p(n_c)$, $n_s$ and $n_c$ are not
+independent: information can be extracted about $n_s$ knowing $n_c$.
+In Fig.~\ref{probdisult} (a) we show the probability distribution of
+$n_s$ for the case where $n_c$.
 
-Having Eq.
-\eqref{numfo} we are able to stablish a dynamic in the system in which we fix the number of photons.
-Fixing the photon number to one and leaving $\mathcal{E}$ as a free parameter, we obtain probability distributions of the number of spontaneous emissions $E_i$ for different mean number of spontaneous emissions just as we see in Fig.
-\ref{probdisult} (a).
-From these probability distributions we can calculate the variance and graph it against the mean value as we see in Fig.
-\ref{probdisult} (b), where we obtain a variance almost equal to the mean value, something which is characteristic of Poisson distributions.
-Finally we can graph the mean value of spontaneous emissions against the number of cavity emissions considering standard deviation in order to have a better grasp of the certainty in the estimations, something that is shown in Fig.
-\ref{graph}.
+In Fig.~\ref{probdisult} (b), where we obtain a variance almost equal
+to the mean value, something which is characteristic of Poisson
+distributions.
+
+\begin{center}
+\begin{figure*}[!t]
+\includegraphics[scale = 0.7]{newerrorppp.pdf}
+\caption{(a) Probability distributions for different mean number of
+  spontaneous emissions $\mu$; (b) Calculation of variance with
+  respect to the mean number of sponatenous emissions $\mu$. In both
+  cases we consider $\expval{n} \approx 1$, $\gamma = 1.0$ ,
+  $\kappa = g = 0.1$ and
+  $\mathcal{E} = \kappa |\langle n \rangle|[1 + 2g^2/\gamma
+  \kappa]$.} \label{error2}
+\end{figure*}
+\end{center}
+
+\begin{center}
+\begin{figure*}
+\begin{center}
+\includegraphics[scale = 0.7]{lastgraph1.pdf}
+\caption{\small{Mean value of spontaneous emissions after post-selection, fixing $\expval{n} \approx 1$, $\gamma =$ 1.0, $g = $ 0.1, and with  $\mathcal{E} =  \kappa |\langle n \rangle|[1 + 2g^2/\gamma \kappa]$ and with tf = 500.
+(a) We consider $\kappa = $0.05 which has a correlation value around $0.1$; (b) we consider $\kappa = $1.0, which has a correlation value around $0.01$.}} \label{probdisult}
+\end{center}
+\end{figure*}
+\end{center}
 
@@
 
-\begin{center}
-\begin{figure*}[!t]
-\begin{center}
-\includegraphics[scale = 0.7]{lastgraph1.pdf}
-\caption{\small{Mean value of spontaneous emissions after post-selection, fixing $\expval{n} \approx 1$, $\gamma =$ 1.0, $g = $ 0.1, and with  $\mathcal{E} =  \kappa |\langle n \rangle|[1 + 2g^2/\gamma \kappa]$ and with tf = 500.
-(a) We consider $\kappa = $0.05 which has a correlation value around $0.1$; (b) we consider $\kappa = $1.0, which has a correlation value around $0.01$.}} \label{probdisult}
-\end{center}
-\end{figure*}
-\end{center}
 The results are shown in Fig. \ref{corrxy}. We see a maximum

### 2019-12-18 newpaper.tex
Quase listo. Leer todos con cuidado

@@
 physical arrangement, one could try to estimate the number of
-spontaneous emissions of the atom --which are emitted in modes that
-are not cavity modes and therefore escape the cavity to its side-- by
-measuring the photons that leak through one of the cavity mirrors. In
-the case that a correlation exists between the two quantities, we can
-count the number of photons that leak the cavity through its mirror,
-which is easy to measure, to find information about the number of
-photons emitted into the other modes (spontaneus emission), which are
-difficult to measure.
+spontaneous emissions of the atom --photons that are emitted in modes
+that are not cavity modes and therefore escape the cavity to its
+side-- by measuring the cavity emissions --photons that leak through
+one of the cavity mirrors. In the case that a correlation exists
+between the two quantities, we can count the number of photons that
+leak the cavity through its mirror, which is easy to measure, to find
+information about the number of photons emitted into the other modes
+(spontaneous emission), which are difficult to measure.
 
@@
 photon, emitted from the atom into the cavity mode, leaks the cavity,
-it will interact with the atom for some time. This interaction creates
-a correlation between photons that leak the cavity through its mirror
-and photons that are emitted from the atom to the cavity side
-(spontaneus emissions).
+it will interact with the atom for some time. This interaction could
+create a correlation between photons that leak the cavity through its
+mirror and photons that are emitted from the atom to the cavity side
+(spontaneous emissions).
 
-We use quantum trajectories theory to calculate the correlation between
-different emission channels. A quantum trajectory is the description
-of a continuously monitored quantum system conditioned on a particular
-past history of coherent evolution and collapse
-\cite{Carmichael1993Open}. These trajectories are simulated through a
-stochastic process, which define the times when the collapses occur.
-Each trajectory gives us the number of photon emitted in each channel.
-Simulating a large number of trajectories and registering the number
-of photon emissions into the two channels, we obtain its correlation.
-The correlation varies with the cavity linewidth and the atom-cavity
-coupling. For a very bad cavity we recover the free space result:
-there is no correlation between the two channels.
+We use quantum trajectories to calculate the joint probability of the
+number of spontaneus emissions and the number of cavity emission. A
+quantum trajectory describes a continuously monitored quantum system
+\cite{Carmichael1993Open}. In our case each trajectory gives the
+number of photons emitted in each channel. Simulating a large number
+of trajectories and registering the number of photon emissions into
+the two channels, we obtain its joint probability distribution and
+their correlation. The correlation varies with the cavity linewidth
+and the atom-cavity coupling. For a very bad cavity we recover the
+free space result: there is no correlation between the two channels.
 
@@
 theoretical model is presented in section \ref{sc:drivenjc}. In
-section \ref{sc:distributions} we obtain join probability distribution
-of the the number of spontaneous and cavity emissions. In section
-\ref{sc:correlation} we calculate the correlation between the two
-variables. Concluding remarks are given in section
+section \ref{sc:distributions} we obtain the joint probability
+distribution of the  number of spontaneous and cavity emissions. In
+section \ref{sc:correlation} we calculate the correlation between the
+two variables. Concluding remarks are given in section
 \ref{sc:conclusions}
@@
 \end{equation}
-where $V_Q$ is the mode volume , $d$ is the atomic dipole , and
-$\epsilon_0$ is the permitivity of free space. $\mathcal{E}$ is a term
+where $V_Q$ is the mode volume, $d$ is the atomic dipole, and
+$\epsilon_0$ is the permittivity of free space. $\mathcal{E}$ is a term
 proportional to the coherent field amplitude. Dissipation is
@@
 rate. The evolution between jumps is given by $H=H_s+H_{nh}$. This
-evolution is interrumped by spontaneus emission by the atom or when a
+evolution is interrupted by spontaneous emission by the atom or when a
 photon leaks the cavity.
 
-We now summarize te quantum trajectory formalism \cite{bla} that we
+We now summarize the quantum trajectory formalism \cite{bla} that we
 use to solve the system. Each quantum trajectory is simulated as
-folllows. We start with a state which represents a ground state of the
+follows. We start with a state which represents a ground state of the
 atom with no photons in the cavity,
@@
 \end{equation}
-The evolution of the state through the schrödinger equation will be
+The evolution of the state through the Schrodinger equation will be
 interrupted by a quantum jump – an abrupt change on our state in which
-a photoemission has ocurred. The probability for such quantum jump to
+a photoemission has occurred. The probability for such quantum jump to
 happen, during the time step $\delta t$, is given by the collapse
@@
   different number of cavity photons. Parameters $\mathcal{E}  =
-  \kappa = \gamma = g = 1$, $100,000$ quantum trajectories. } \label{probdiss}
+  \kappa =  g = 1\gamma$, $100,000$ quantum trajectories. } \label{probdiss}
 \end{figure}
@@
 $t/\delta t$ steps. For each trajectory we count the number of quantum
-jumps, the jumps correponding to operator $a$ reduces the number of
+jumps, the jumps corresponding to operator $a$ reduces the number of
 photons inside the cavity and corresponds to a photon that leak the
@@
 from the cavity is $n_c$. This simulate the physical situation where
-we count the number of spontaneus photons until the moment where the
+we count the number of spontaneous photons until the moment where the
 number of leaked photons from the cavity is $n_c$. It is impossible to
 know in advance how long it takes to the cavity to leak $n_c$ photons,
-thus the time each quantum trajectory is evolved is not fixed. Second,
-we fix the time each quantum trajectory is evolved and count the
-number of spontaneus emissions $n_s$, and cavity emissions $n_c$. From
-the set of quantum trajectories evolved a fixed time, we calculate the
-joint probability $p(n_s,n_c)$, of finding $n_s$ spontaneous emissions
-and $n_c$ cavity emissions. Using $p(n_s,n_c)$ we calculate the
-correlations between the two random variables. This correlation is a
-measure of how much information we can obtain about $n_s$ if we know
-$n_c$.
+thus the duration of each quantum trajectory is not fixed. Second, we
+fix the duration of each quantum trajectory and count the number of
+spontaneous emissions $n_s$, and cavity emissions $n_c$. From the set
+of quantum trajectories evolved a fixed time, we calculate the joint
+probability $p(n_s,n_c)$, of finding $n_s$ spontaneous emissions and
+$n_c$ cavity emissions. Using $p(n_s,n_c)$ we calculate the
+conditional probability $p(n_s|n_c)$, and the correlations between the
+two random variables. This correlation is a measure of how much
+information we can obtain about $n_s$ if we know $n_c$.
 
@@
 $\expval{\sigma_z}$ that correspond to the cavity field, atomic
-coherence, and atomic inversion respectively \cite{Alsing_1991}. For
-the case of the driven Jaynes-Cummings system, these equations are
+coherence, and atomic inversion respectively \cite{Alsing_1991}. In
+our case, these equations are
 \begin{subequations} \label{maxbloch}
@@
 that the mean number of photons inside the cavity is $1/9$. The
-results are shown in Fig.~\ref{probdiss}. As the number of leaked
-photons increases, the mean number of spontaneous emissions increases.
-This result is expected, because the number of leaked photons is
-correlated with the time we are counting spontaneus emission photons
-from a driven atom: the larger the number of leaked photons the larger
-the time we measure spontaneous emitted photons, which implies a
-larger mean number of emitted photons. Also, as shown in
-Fig~\ref{graph}, the probability distribution is wider as the number
-of leaked photons increases, this implies less accuracy guessing the
-number of spontaneus emission. If we know the cavity drive, this
-results does not imply that we can learn something extra about the
-number of spontaneous emissions knowing the number of photons leaked
-from the cavity; it is clear that when we increase the time window
-where we count photons, both, the number of leaked photons and the
-number of spontaneous emissions, increases.
+results are shown in Fig.~\ref{probdiss}. As the number of cavity
+emissions increases, the mean number of spontaneous emissions
+increases. This result is expected, because the number of cavity
+emissions is correlated with the time we are counting spontaneous
+emission photons from the atom: the larger the number of cavity
+emissions the larger the time we count spontaneous emitted photons,
+which implies a larger mean number of emitted photons. Also, as shown
+in Fig~\ref{graph}, the probability distribution is wider as the
+number of leaked photons increases, this implies less accuracy
+guessing the number of spontaneous emission. If we know the cavity
+drive, this results does not imply that we can learn something extra
+about the number of spontaneous emissions knowing the number of
+photons leaked from the cavity; it is clear that when we increase the
+time window where we count photons, both, the number of cavity emissions
+and the number of spontaneous emissions, increases.
 
@@
 \centering
-\includegraphics[scale = 0.5]{newsigmaeng.pdf}
-\caption{Average number of spontaneous emissions $\pm \sigma$ with respect to cavity emissions, under parameters $\expval{n} \approx 1$, $\gamma = 1$ , $\kappa = g = 0.1$ and $\mathcal{E} =  \kappa |\langle n \rangle|[1 + 2g^2/\gamma \kappa]$.}
+\includegraphics[scale = 0.5]{newsigma1.pdf}
+\caption{Average number of spontaneous emissions with its standard
+  deviation as a function of cavity emissions. Parameters: $\expval{n} \approx 1$, $\kappa = g = 0.1\gamma$}
 \label{graph}
@@
 We consider the set of quantum trajectories of the same duration. This
-corresponds to fixing the time we measure photons. Each set of quantum
-trajectories with the same duration is labelled with its mean number
-of spontaneous emitted photons $\mu$. We consider the case where we
-fix the mean number of photons inside the cavity to $1$. As shown by
+corresponds to fixing the time we count photons. Each set of quantum
+trajectories with the same duration is labeled with its mean number
+of spontaneous emitted photons $\langle n_s\rangle$, given the system
+parameters, a larger $\langle n_s\rangle$ implies quantum trajectories
+with larger duration. We consider the case where we fix the mean
+number of photons inside the cavity to $1$. As shown by
 Eq.~(\ref{numfo}), this number depends on the drive, and cavity and
@@
 In Fig.~\ref{error2}(a) the probability distribution of spontaneous
-emitted photons is shown for different mean values. As it is shown in
-Fig.~\ref{error2}(b), the width of the distribution increases linearly
-with the mean number of spontaneus emission. This behaviour does not
-imply any correlation between the number of spontaneus emissions and
-cavity emissions.
+emitted photons is shown for different duration of the quantum
+trajectories. As it is shown in Fig.~\ref{error2}(b), the width of the
+distribution increases linearly with the mean number of spontaneous
+emissions. This behavior does not imply any correlation between the
+number of spontaneous emissions and cavity emissions.
 
@@
 number of cavity emissions is a fixed number $n_c$, and plot
-$p(n_s|n_c)$, the probability distribution of the number of spontaneus
+$p(n_s|n_c)$, the probability distribution of the number of spontaneous
 emissions $n_s$, under the condition that $n_c$ cavity emissions
@@
 independent: information can be extracted about $n_s$ knowing $n_c$.
-In Fig.~\ref{probdisult} (a) we show the probability distribution of
-$n_s$ for the case where $n_c$.
-
-In Fig.~\ref{probdisult} (b), where we obtain a variance almost equal
-to the mean value, something which is characteristic of Poisson
-distributions.
+An example of this is shown in Fig.~\ref{probdisult}(a), where we
+show $p(n_s|n_c)$, the probability distribution of $n_s$ postselected
+to the case where the number of cavity emissions is
+$n_c=\langle n_c \rangle$, and $n_c=\langle n_c \rangle\pm\sigma$. We
+see a positive correlation between the two random variables: the
+maximum of the probability distribution increases (decreases) if we
+postselect the trajectories with a larger than the mean (smaller than
+the mean) number of cavity emissions. In Fig.~\ref{probdisult}(b), we
+show that for a cavity with large $\kappa$, the change in the
+probability distribution $p(n_s|n_c)$ is much smaller than in the case
+for small $\kappa$. When
+$\kappa\rightarrow\infty$, there are no correlation between the two
+channels and $p(n_s|n_c)=p(n_s)p(n_c)$.
+In the next section we calculate the correlation between $n_s$ and
+$n_c$ for different $\kappa$.
 
@@
 \begin{figure*}[!t]
-\includegraphics[scale = 0.7]{newerrorppp.pdf}
+\includegraphics[scale = 0.5]{newerrorppp.pdf}
 \caption{(a) Probability distributions for different mean number of
-  spontaneous emissions $\mu$; (b) Calculation of variance with
-  respect to the mean number of sponatenous emissions $\mu$. In both
-  cases we consider $\expval{n} \approx 1$, $\gamma = 1.0$ ,
-  $\kappa = g = 0.1$ and
-  $\mathcal{E} = \kappa |\langle n \rangle|[1 + 2g^2/\gamma
-  \kappa]$.} \label{error2}
+  spontaneous emissions $\langle n_s\rangle=\bar{n}_s$; (b)
+  Variance of the random variable $n_s$ with respect to the mean number of
+  spontaneous emissions. In both cases we consider
+  $\expval{n} \approx 1$,  $\kappa = g = 0.1\gamma$.} \label{error2}
 \end{figure*}
@@
 \begin{center}
-\includegraphics[scale = 0.7]{lastgraph1.pdf}
-\caption{\small{Mean value of spontaneous emissions after post-selection, fixing $\expval{n} \approx 1$, $\gamma =$ 1.0, $g = $ 0.1, and with  $\mathcal{E} =  \kappa |\langle n \rangle|[1 + 2g^2/\gamma \kappa]$ and with tf = 500.
-(a) We consider $\kappa = $0.05 which has a correlation value around $0.1$; (b) we consider $\kappa = $1.0, which has a correlation value around $0.01$.}} \label{probdisult}
+\includegraphics[scale = 0.5]{lastgraph1.pdf}
+\caption{Probability distribution of spontaneous emissions
+  postselected to the condition that $n_c$ cavity emissions happened
+  $p(n_s|n_c)$; observe, in both figures, the change in the
+  probability distribution for spontaneous emissions for different
+  postselections. (a) $\kappa = 0.05\gamma$,
+  $\langle n_c\rangle=\bar{n}_c=50$, $\sigma=7$; (b) 
+  $\kappa = 1.0$, $\langle n_c\rangle=\bar{n}_c=1000$, $\sigma=28$.
+  Other parameters $\expval{n} \approx 1$, $g =0.1\gamma$,
+  time of each trajectory: $500/\gamma$. } \label{probdisult}
 \end{center}
@@
 In this section we study the correlation between the number of
-spontaneus emission from the atom, $n_s$, and the number of photons
-that leak the cavity, $n_c$, as a function of the cavity decay rate,
+spontaneous emissions from the atom $n_s$, and the number of photons
+that leak the cavity $n_c$, as a function of the cavity decay rate
 $\kappa$. We expect that when $\kappa\rightarrow\infty$ there would be
 no correlation between these two random variables, since this
-situation will be equivalent to the situation where there is no
+situation is equivalent to the situation where there is no
 cavity.
 
-In order to have a measure of the correlation between emissions in the
-two different channels, we use the Pearson Correlation Coefficient
+In order to calculate the correlation between emissions in the two
+different channels, we use the Pearson correlation coefficient
 \cite{benesty2009pearson}
@@
 \includegraphics[scale = 0.5]{million1.pdf}
-\caption{\small{Calculation of correlation using a time interval, tf = 500, fixing $\expval{n} \approx 1$, $\gamma =$ 1.0, $g = $ 0.1, and with  $\mathcal{E} =  \kappa |\langle n \rangle|[1 + 2g^2/\gamma \kappa]$.}} \label{corrxy}
+\caption{Pearson correlation coefficient as a function of $\kappa$.
+  The duration of the quantum trajectories is  $\gamma t_f = 500$.
+  Other parameters $\expval{n} \approx 1$, $g = 0.1\gamma$.} \label{corrxy}
 \end{center}  
@@
 \includegraphics[scale = 0.5]{million2.pdf}
-\caption{\small{Correlation using different temporal intervals, fixing $\expval{n} \approx 1$, $\gamma =$ 1.0, $g =$ 0.1, and with  $\mathcal{E} =  \kappa |\langle n \rangle|[1 + 2g^2/\gamma \kappa]$.}}  \label{errorzz}
+\caption{Pearson correlation coefficient as a function of $\kappa$ for
+  quantum trajectories with different duration. Parameters:
+  $\expval{n} \approx 1$, $g = 0.1\gamma$.} \label{errorzz}
 \end{center}
@@
 correlation close to $0.1$ for $\kappa/\gamma\approx 0.05$ that
-decreases as $\kappa$ increases. From the figure it looks like the
-correlation goes to zero as $\kappa\rightarrow\infty$. With values for
-$\kappa/\gamma$ lower than $0.05$, we notice that the correlations
-increase stops and a decrease begins. This stop in the increase of the
-correlation is due to the fact that, as we keep decreasing the cavity
-linewidth the number of photons that leaks the cavity decreases
-considerably. In the limit where $\kappa=0$ the two random
+decreases as $\kappa$ increases. The figure is consistent with the
+statement that the correlation goes to zero as
+$\kappa\rightarrow\infty$. With values for $\kappa/\gamma$ lower than
+$0.05$, we notice that the correlations begins to decrease. The reason
+is that, as the cavity linewidth decreases, the number of cavity
+emissions decreases. In the limit where $\kappa=0$ the two random
 variables becomes independent, because the output of $n_c$ is zero
-with probability one. In this case there is no correlation between the two
-random variables.
+with probability one. In this case there is no correlation between the
+two random variables. Fig.~\ref{probdisult}(a), where the change in
+$p(n_s|n_c)$ is larger, corresponds to a correlation around $0.1$;
+Fig.~\ref{probdisult}(b), where the change is small, corresponds to a
+correlation around $0.01$.
 
-In Fig. \ref{errorzz} it is shown that as we increase the temporal
-interval where we count photons, we also see a small increment of the
-correlation, due to the fact that more photons leaks the cavity
-giving information about the system.
-\fxnote{Hay que mejorar las graficas. Las variables tienen que ser
-  mayores y las unidades estan mal}
-
-%In Fig.
-\ref{errorzz} we can appreciate that, as we increase the total temporal interval, the cavity linewidth at which the correlation starts decreasing is smaller.
-This supports the idea that the time that takes for the system in stablishing the number photons will affect the minimum value of cavity linewidth at which the correlation starts decreasing.
-Studying this correlation further, we see how the average number of
-spontaneous emissions varies given the number of cavity emissions during a constant length of time. Making a 
-post-selection around the average number of cavity emissions we make a gaussian
-adjustment for the average number of spontaneous emissions and the corresponding 
-standard deviation. Such results are shown in Fig. \ref{probdisult}, where we notice that
-for the case in which we have a correlation around $0.1$, making a post-selection with a 
-bigger number of cavity emissions turns into an increase of the mean number of spontaneous emissions,
- while the opposite happens for a lower number of cavity emissions. On the other hand, when 
-the correlation is around $0.01$, the change in the average number of spontaneous emissions
-after the post-selection is barely noticeable.
+In Fig. \ref{errorzz} we plot the Pearson correlation coefficient as a
+function of $\kappa/\gamma$ for different durations of the quantum
+trajectories. We observe a small increment of the correlation
+because more photons leaks the cavity, giving information about the
+system.
 
@@
 leaky cavity are correlated. The correlations are produced because the
-cavity breaks the markovian behavior of atomic emission. the presence
+cavity breaks the markovian behavior of atomic emission. The presence
 of correlation between photons measured in different directions is a
-signature of non-markovian behaviour. This correlation also allows us
-to improve the knowledge we know about the probability distribution of
-atomic spontaneus emission if we know the number of photons that leak
-the cavity.
+signature of non-markovian behavior. This correlation allows us to
+improve the knowledge we know about the probability distribution of
+atomic spontaneous emission if we know the number of photons that leak
+the cavity. In the system configuration that we studied the maximum
+correlation is small. Nevertheless, we think that the results
+encourage to explore different configurations where the correlation
+can be larger.
 
@@
 
-\fxnote{Creo que faltan dos cosas en este paper: la correlacion como
-  funcion de $g$ dado $\kappa$ constante. Una grafica mostrando, para
-  un tiempo fijo, como cambia la funcion de probabilidad para
-  emisiones espontaneas como funcion de fotones detectados fuera de la
-  cavida. Es decir: $p(n_s,n_c,t_0)$}
-
 \bibliography{reftesis}% Produces the bibliography via BibTeX.

### 2019-12-19 newpaper.tex
Agregrue agradecimientos
Segunda quase version final

@@
 
-\title{Correlation between different emission channels from an atom inside a leaky driven cavity}% Force line breaks with \\
+\title{Correlation between photons emitted in diferent channels from
+  an atom inside a leaky driven cavity}% Force line breaks with \\
 
@@
  %Lines break automatically or can be forced with \\
-\author{Pablo Barberis}%
+\author{Pablo Barberis-Blostein}%
 \affiliation{Instituto de Investigaciones en Matemáticas Aplicadas y en Sistemas, Universidad Nacional Autónoma de México, Ciudad Universitaria, 04510, CDMX, México.}
@@
 \begin{abstract}
-A two level atom in free space does not show any correlation between
-  photons emitted in different directions. We consider a two level
+  Photons emitted by a driven two level atom in free space do not show
+  correlation between different directions. We consider a two level
   atom inside a driven leaky cavity. We consider two atomic emission
@@
   between photons emitted into cavity modes and that leak the cavity
-  through its mirror, with photons that are emitted into the rest of
-  the modes. We find that the cavity generates a correlation between
-  the two emission channels.
+  through its mirror, with photons that are emitted into the other
+  modes. We find that the cavity generates a correlation between the
+  two emission channels.
 \end{abstract}
@@
 
-Spontaneous emission is a phenomenon that has been studied since the
-early XX century \cite{10.2307/94746, 1917PhyZ...18..121E}. One of the
-main characteristics of spontaneous emission is that the exact time of
-emission, as well as the direction in which the photon is emitted, is
-random, which difficults its measurement. On the other hand, photons
-emitted from a cavity mirror are easier to measure because we know
-their direction \cite{326305, doi:10.1063/1.113345}. The randomness of
-the direction in which the photons are emitted by atoms in free space
-difficults photon counting experiments. To sort out this difficulty
-one could think of a physical arrangement in which a two-level atom is
-coupled to a driven cavity, as it is shown in Fig. \ref{asa}. In this
-physical arrangement, one could try to estimate the number of
-spontaneous emissions of the atom --photons that are emitted in modes
-that are not cavity modes and therefore escape the cavity to its
-side-- by measuring the cavity emissions --photons that leak through
-one of the cavity mirrors. In the case that a correlation exists
-between the two quantities, we can count the number of photons that
-leak the cavity through its mirror, which is easy to measure, to find
-information about the number of photons emitted into the other modes
-(spontaneous emission), which are difficult to measure.
+Spontaneous emission has been studied since the early XX century
+\cite{10.2307/94746, 1917PhyZ...18..121E}. One its main
+characteristics is that the exact time of emission, as well as the
+direction in which the photon is emitted, is random, which difficults
+its measurement. On the other hand, photons that leak a cavity mirror
+are easier to measure because we know their direction \cite{326305,
+  doi:10.1063/1.113345}. The randomness of the direction in which the
+photons are emitted by atoms in free space difficults photon counting
+experiments. To sort out this difficulty one could think of a physical
+arrangement in which a two-level atom is coupled to a driven cavity,
+as it is shown in Fig. \ref{asa}. In this physical arrangement, we
+have two emission channels: spontaneous emissions of the atom
+--photons that are emitted in modes that are not cavity modes and
+therefore escape the cavity to its side-- and cavity emissions
+--photons that leak through one of the cavity mirrors. In the case
+that a correlation exists between the two channels, we can count the
+number of photons that leak the cavity through its mirror, which is
+easy to measure, to find information about the number of photons
+emitted into the other modes (spontaneous emission), which are
+difficult to measure.
 
@@
 the fact that the atom's environment memory of previous interactions
-with it, is very short; this is what justify the markovian
+with it, is very short; this is what justifies the markovian
 approximation \cite{daley2014quantum}. Two atomic emissions would be
@@
 
-For an atom in free space, knowing the number of photons emitted in
-some region of the space during some time does not give any
-information on the number of photons emitted in other region of the
-space. Nevertheless, for the case of an atom inside a cavity, before a
-photon, emitted from the atom into the cavity mode, leaks the cavity,
-it will interact with the atom for some time. This interaction could
-create a correlation between photons that leak the cavity through its
-mirror and photons that are emitted from the atom to the cavity side
-(spontaneous emissions).
+For an atom inside a cavity, before a photon, emitted from the atom
+into the cavity mode, leaks the cavity, it will interact with the atom
+for some time. This interaction could create a correlation between
+photons that leak the cavity through its mirror and photons that are
+emitted from the atom to the cavity side (spontaneous emissions).
 
@@
 \begin{center}
-\begin{figure*}\label{asa}
-\begin{center}
+\begin{figure*}
 \includegraphics[scale = 0.65]{newimagepaper.pdf}
-%\includegraphics[scale = 0.45]{image_paper222.png}
 \caption{A driven atom in free space (a) and inside a driven leaky
@@
   there is no correlation between $m$ and $n$. For the atom inside the
-  leaky cavity we find a correlation between $m$ and $n$.}
-\end{center}
+  leaky cavity we find a correlation between $m$ and $n$.}\label{asa}
 \end{figure*}
@@
 %\end{equation}
-The Hamiltonian of this system, in the rotating wave approximation is
+The Hamiltonian of this system, in the rotating wave approximation, is
 given by
@@
 \end{equation}
-while the coupling between atom and cavity, and cavity and coherent
+$\omega$ is the cavity mode frequency and the atomic transition
+frequency. The atom is in resonance with the cavity mode. 
+The coupling between atom and cavity, and cavity and coherent
 field are
@@
 where $V_Q$ is the mode volume, $d$ is the atomic dipole, and
-$\epsilon_0$ is the permittivity of free space. $\mathcal{E}$ is a term
-proportional to the coherent field amplitude. Dissipation is
-introduced by the following non-hermitian Hamiltonian
+$\epsilon_0$ is the permittivity of free space. $\mathcal{E}$ is a
+term proportional to the coherent field that drives the cavity in
+resonance. Dissipation is introduced by the following non-hermitian
+Hamiltonian
 \begin{equation} \label{nh}
@@
 $\ket{\phi(t = 0)} = \ket{\downarrow} \times \ket{0}$, we evolve it
-with the Schrödinger equation through some time $\delta t$, using the
+with the Schr\"odinger equation through some time $\delta t$, using the
 non-hermitian Hamiltonian
@@
 \cite{Sakurai:1167961}. For the next step we repeat the procedure
-using the resulting state for this step. One quantum trajectory of
-total time $t$ is obtained after repeating the previous procedure
-$t/\delta t$ steps. For each trajectory we count the number of quantum
-jumps, the jumps corresponding to operator $a$ reduces the number of
-photons inside the cavity and corresponds to a photon that leak the
-cavity. The jumps corresponding to operator $\sigma_-$ interrumps its
-unitary evolution and send it back to the ground state, it corresponds
-to a spontaneous emission. The procedure to register emissions in the
-two different channels is summarized in algorithm. \ref{alg1}.
+using the new state. One quantum trajectory of total time $t_f$ is
+obtained after repeating the previous procedure $t_f/\delta t$ steps.
+For each trajectory we count the number of quantum jumps, the jumps
+corresponding to operator $a$ reduces the number of photons inside the
+cavity and corresponds to a photon that leak the cavity. The jumps
+corresponding to operator $\sigma_-$, send the atom back to the ground
+state and corresponds to a spontaneous emission. The procedure to
+register emissions in the two different channels is summarized in
+algorithm. \ref{alg1}.
 
 We realize a large number of these trajectories and keep track of the
-numbers of emission for each channel, with this data we can calculate
-probability distributions that relate these two quantities.
+numbers of emission for each channel, with this data we calculate
+the joint probability distribution of the number of emissions in each
+of the two channels.
 
@@
 \end{equation}
-When $\gamma \gg g$, the expected value of the number of photons in
+When $\gamma \gg g$, the expected value of the number of photons inside
 the cavity is 
@@
 emissions is correlated with the time we are counting spontaneous
-emission photons from the atom: the larger the number of cavity
-emissions the larger the time we count spontaneous emitted photons,
+emission from the atom: the larger the number of cavity
+emissions the larger the time we count spontaneous emission,
 which implies a larger mean number of emitted photons. Also, as shown
@@
 trajectories with the same duration is labeled with its mean number
-of spontaneous emitted photons $\langle n_s\rangle$, given the system
+of spontaneously emitted photons $\langle n_s\rangle$, given the system
 parameters, a larger $\langle n_s\rangle$ implies quantum trajectories
@@
 Now we focus in the case, where given a set of quantum trajectories
-with fixed duration, we postselect all the trajectories where the
+with fixed duration $t_f$, we postselect all the trajectories where the
 number of cavity emissions is a fixed number $n_c$, and plot
@@
 to the case where the number of cavity emissions is
-$n_c=\langle n_c \rangle$, and $n_c=\langle n_c \rangle\pm\sigma$. We
+$n_c=\langle n_c \rangle$, and $n_c=\langle n_c \rangle\pm 3 \sigma$. We
 see a positive correlation between the two random variables: the
@@
 
-The results are shown in Fig. \ref{corrxy}. We see a maximum
-correlation close to $0.1$ for $\kappa/\gamma\approx 0.05$ that
-decreases as $\kappa$ increases. The figure is consistent with the
-statement that the correlation goes to zero as
+The results are shown in Fig. \ref{corrxy}. We observe a maximum
+correlation, close to $0.1$, for $\kappa/\gamma\approx 0.05$. From
+there the correlation decreases as $\kappa$ increases. The figure is
+consistent with the statement that the correlation goes to zero as
 $\kappa\rightarrow\infty$. With values for $\kappa/\gamma$ lower than
@@
 
+\begin{acknowledgments}
+This work was supported by DGAPA-UNAM under grant PAPIIT-IG120518.
+\end{acknowledgments}
+
 \bibliography{reftesis}% Produces the bibliography via BibTeX.

### 2019-12-20 newpaper.tex
Version quase final, falta aprobacion de Guillermo
Version para mandar a EPJ D

@@
 Spontaneous emission has been studied since the early XX century
-\cite{10.2307/94746, 1917PhyZ...18..121E}. One its main
+\cite{10.2307/94746, 1917PhyZ...18..121E}. One of its main
 characteristics is that the exact time of emission, as well as the
@@
 We use quantum trajectories to calculate the joint probability of the
-number of spontaneus emissions and the number of cavity emission. A
+number of spontaneus emissions and the number of cavity emissions. A
 quantum trajectory describes a continuously monitored quantum system
@@
 \caption{Probability distribution of spontaneous emissions for
-  different number of cavity photons. Parameters $\mathcal{E}  =
-  \kappa =  g = 1\gamma$, $100,000$ quantum trajectories. } \label{probdiss}
+  different number of cavity photons. Parameters: $\expval{n} \approx 1$, $\kappa = g = 0.1\gamma$. } \label{probdiss}
 \end{figure}
@@
 the set of quantum trajectories where the number of leaked photons
-from the cavity is $n_c$. This simulate the physical situation where
+from the cavity is $n_c$. This simulates the physical situation where
 we count the number of spontaneous photons until the moment where the
@@
 emission when a fixed number of photons leaked the cavity. We assume
-that the mean number of photons inside the cavity is $1/9$. The
+that the mean number of photons inside the cavity is $1$. The
 results are shown in Fig.~\ref{probdiss}. As the number of cavity
@@
 emissions decreases. In the limit where $\kappa=0$ the two random
-variables becomes independent, because the output of $n_c$ is zero
+variables become independent, because the output of $n_c$ is zero
 with probability one. In this case there is no correlation between the
@@
 \section{Conclusions}\label{sc:conclusions}
-Atomic emission in cavity and non-cavity modes of an atom inside a
+Atomic emissions in cavity and non-cavity modes of an atom inside a
 leaky cavity are correlated. The correlations are produced because the

### 2021-08-11 EPJD/newpaper.tex
Modificacion misteriosa

--- 2019-12-20 newpaper.tex
@@
-% ****** Start of file apssamp.tex ******
-%
-%   This file is part of the APS files in the REVTeX 4.2 distribution.
-%   Version 4.2a of REVTeX, December 2014
-%
-%   Copyright (c) 2014 The American Physical Society.
-%
-%   See the REVTeX 4 README file for restrictions and more information.
-%
-% TeX'ing this file requires that you have AMS-LaTeX 2.0 installed
-% as well as the rest of the prerequisites for REVTeX 4.2
-%
-% See the REVTeX 4 README file
-% It also requires running BibTeX. The commands are as follows:
-%
-%  1)  latex apssamp.tex
-%  2)  bibtex apssamp
-%  3)  latex apssamp.tex
-%  4)  latex apssamp.tex
-%
-\documentclass[%
- reprint,
-%superscriptaddress,
-%groupedaddress,
-%unsortedaddress,
-%runinaddress,
-%frontmatterverbose, 
-%preprint,
-%preprintnumbers,
-%nofootinbib,
-%nobibnotes,
-%bibnotes,
- amsmath,amssymb,
- aps, 
-%pra,
-%prb,
-%rmp,
-%prstab,
-%prstper,
-%floatfix,
-]{revtex4-1}
-
+\documentclass[epj,final]{svjour}
 \usepackage{hyperref}
@@
 \usepackage{physics}
-\usepackage[draft,inline,nomargin]{fixme} \fxsetup{theme=color}
-%\usepackage{algorithm}
 \usepackage{algorithmic}
@@
 \usepackage{bm}% bold math
-%\usepackage{hyperref}% add hypertext capabilities
-%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
-%\linenumbers\relax % Commence numbering lines
-
-%\usepackage[showframe,%Uncomment any one of the following lines to test 
-%%scale=0.7, marginratio={1:1, 2:3}, ignoreall,% default settings
-%%text={7in,10in},centering,
-%%margin=1.5in,
-%%total={6.5in,8.75in}, top=1.2in, left=0.9in, includefoot,
-%%height=10in,a5paper,hmargin={3cm,0.8in},
-%]{geometry}
-
+\usepackage[square,numbers]{natbib}
+\bibliographystyle{unsrtnat}
 \begin{document}
 
-\preprint{APS/123-QED}
-
-\title{Correlation between photons emitted in diferent channels from
+\title{Correlation between photons emitted in different channels from
   an atom inside a leaky driven cavity}% Force line breaks with \\
 
-\author{Guillermo Preisser}
- \email{Corresponding author e-mail: guillermo.preisser@uabc.edu.mx}
- %Lines break automatically or can be forced with \\
-\author{Pablo Barberis-Blostein}%
-\affiliation{Instituto de Investigaciones en Matemáticas Aplicadas y en Sistemas, Universidad Nacional Autónoma de México, Ciudad Universitaria, 04510, CDMX, México.}
+\author{Guillermo Preisser \and  Pablo Barberis-Blostein}
+ \mail{guillermo.preisser@uabc.edu.mx}
 
-\date{\today}% It is always \today, today,
-             %  but any date may be explicitly specified
+%\offprints{}
+ \institute{Instituto de Investigaciones en Matem\'aticas Aplicadas y en
+   Sistemas, Universidad Nacional Aut\'onoma de M\'exico, Ciudad
+   Universitaria, 04510, CDMX, México.}
 
-\begin{abstract}
+\date{\today}
+
+\abstract{
   Photons emitted by a driven two level atom in free space do not show
@@
   modes. We find that the cavity generates a correlation between the
-  two emission channels.
-\end{abstract}
+  two emission channels.}
 
-%\keywords{Suggested keywords}%Use showkeys class option if keyword
-                              %display desired
+\titlerunning{Correlations in an atom inside a leaky driven cavity}
 \maketitle
@@
 Spontaneous emission has been studied since the early XX century
-\cite{10.2307/94746, 1917PhyZ...18..121E}. One of its main
+\cite{10.2307/94746} \cite{1917PhyZ...18..121E}. One of its main
 characteristics is that the exact time of emission, as well as the
@@
 its measurement. On the other hand, photons that leak a cavity mirror
-are easier to measure because we know their direction \cite{326305,
-  doi:10.1063/1.113345}. The randomness of the direction in which the
-photons are emitted by atoms in free space difficults photon counting
-experiments. To sort out this difficulty one could think of a physical
-arrangement in which a two-level atom is coupled to a driven cavity,
-as it is shown in Fig. \ref{asa}. In this physical arrangement, we
-have two emission channels: spontaneous emissions of the atom
---photons that are emitted in modes that are not cavity modes and
-therefore escape the cavity to its side-- and cavity emissions
+are easier to measure because we know their direction
+\cite{326305} \cite{doi:10.1063/1.113345}. The randomness of the direction in
+which the photons are emitted by atoms in free space difficults photon
+counting experiments. To sort out this difficulty one could think of a
+physical arrangement in which a two-level atom is coupled to a driven
+cavity, as it is shown in Fig. \ref{asa}. In this physical
+arrangement, we have two emission channels: spontaneous emissions of
+the atom --photons that are emitted in modes that are not cavity modes
+and therefore escape the cavity to its side-- and cavity emissions
 --photons that leak through one of the cavity mirrors. In the case
@@
 We use quantum trajectories to calculate the joint probability of the
-number of spontaneus emissions and the number of cavity emissions. A
+number of spontaneous emissions and the number of cavity emissions. A
 quantum trajectory describes a continuously monitored quantum system
@@
 with the atomic transition and the cavity mode.
-% In order to account for
-% dissipation one may use a non-hermitian Hamiltonian to describe the
-% system \cite{bla}. Using this description for the system will turn
-% useful at the moment of using quantum trajectory theory. Such
-% Hamiltonian can be separated into hermitian and non-hermitian terms.
-%\begin{equation}
-%H = H_s - \frac{i\hbar}{2}\sum_m C^\dagger_n C_n .
-%\end{equation}
 The Hamiltonian of this system, in the rotating wave approximation, is
@@
 \makeatletter
-%\DeclareCaptionLabelFormat{numberless}{\ALG@name#1}
-%\captionsetup[algorithm]{labelformat=numberless} 
 \makeatother
@@
 simulate that a quantum jump has happened, by acting with one of the
-collapse operators $a$ or $\sigma_-$ and renormalizating the obtained
+collapse operators $a$ or $\sigma_-$ and renormalizing the obtained
 state. The operator that will act on the state will be given according
@@
 \end{center}
-%kncrease or increases
-
-%\begin{center}
-%\begin{figure}[h!]
-%\begin{center}
-%\includegraphics[scale = 0.7]{lastgraph.pdf}
-%\caption{\small{Mean value of spontaneous emissions after post-selection, fixing $\expval{n} \approx 1$, $\gamma =$ 1.0, $g = \kappa =$ 0.1, and with  $\mathcal{E} =  \kappa |\langle n \rangle|[1 + 2g^2/\gamma \kappa]$.}}  \label{errorzz}
-%\end{center}
-%\end{figure}
-%\end{center}
 
@@
 
-% In this work we considered a driven Jaynes-Cummings system. We made a
-% program in which, through the use of quantum trajectory theory, we
-% were able to obtain probability distributions that relate the number
-% of spontaneous emissions given certain number of cavity emissions.
-% Through the probability distributions we obtained estimations for the
-% number of spontaneous emissions by measuring cavity emissions,
-% considering the correspondent error. Finally we study the existing
-% correlation where we saw how this correlation decreases as we increase
-% the cavity linewidth. However, if we try with values for
-% $\kappa/\gamma < 0.1$, there comes a point where the increase stops
-% and we see a decrease. We believe this is related to the fact that if
-% we use enough small values of $\kappa$ there will come a point where
-% the emission of photons will be too low and this will imply a decrease
-% in the correlation. The results in this work provide a tool that could
-% be useful in the manipulation of single photons product of spontaneous
-% emission, and provide insight into the physical behavior of the driven
-% Jaynes-Cummings model.
+\section{Authors contributions}
+All the authors were involved in the preparation of the manuscript.
+All the authors have read and approved the final manuscript.
 
-\begin{acknowledgments}
+\begin{acknowledgement}
 This work was supported by DGAPA-UNAM under grant PAPIIT-IG120518.
-\end{acknowledgments}
+\end{acknowledgement}
 
-\bibliography{reftesis}% Produces the bibliography via BibTeX.
+\bibliography{../reftesis}% Produces the bibliography via BibTeX.
 

### 2021-08-11 newpaper.tex
Un par de errores ortograficos

@@
 
-\title{Correlation between photons emitted in diferent channels from
+\title{Correlation between photons emitted in different channels from
   an atom inside a leaky driven cavity}% Force line breaks with \\
@@
 
-\begin{acknowledgments}
+\begin{acknowledgement}
 This work was supported by DGAPA-UNAM under grant PAPIIT-IG120518.
-\end{acknowledgments}
+\end{acknowledgement}
 
